---
title: "R Notebook"
output: html_notebook
---

This document follows Inundation_hatchsuccess_v1.Rmd. Data were extracted in the previous step. In this analysis, I sue Random Forest to predict hatching success. 

```{r}
# clear the workspace and bring in libraries
rm(list=ls())
library(tidyverse)
library(party)
library(betareg)
library(jagsUI)
library(bayesplot)
library(loo)

source("Dunstan_Inundation_fcns.R")

save.fig <- F
save.file <- F

MCMC.params <- list(n.samples = 20000,
                    n.burnin = 15000,
                    n.thin = 5,
                    n.chains = 5)

```



```{r}
inund.cols <- cols(fid = col_integer(),
                   Nest_UID = col_character(),
                   Northings = col_double(),
                   Eastings = col_double(),
                   Nest_Elevation = col_double(),
                   Berm_Dist = col_double(),
                   Habitat = col_character(),
                   Sector = col_character(),
                   Island_Aspect = col_character(),
                   ID_closest_logger = col_character(),
                   Season = col_character(),
                   Survey = col_character(),
                   Incubation_Start = col_date(format = "%Y-%m-%d"),
                   Incubation_Finish = col_date(format = "%Y-%m-%d"),
                   Date_dug = col_date(format = "%Y-%m-%d"),
                   Hatched = col_integer(),
                   Live_hatchlings = col_integer(),
                   Dead_hatchlings = col_integer(),
                   Phase_1 = col_integer(),
                   Phase_2 = col_integer(),
                   Phase_3 = col_integer(),
                   Phase_4 = col_integer(),
                   Phase_5 = col_integer(),
                   Phase_6 = col_integer(),
                   Decomposed = col_integer(),
                   Total_unhatched = col_integer(),
                   Total_clutch = col_integer(),
                   prop_success = col_double(),
                   sector = col_character(),
                   season = col_character(),
                   Max_Height = col_double(),
                   n_Inundation = col_integer(),
                   Max_Inund_Duration_Hr = col_double(),
                   Total_Inund_Duration_Hr = col_double(),
                   Mean_Inund_Duration_Hr = col_double(),
                   Prop_Inund_Duration = col_double(),
                   SD_Inund_Duration_Hr = col_double(),
                   Mean_Max_Height_Per_Event = col_double(),
                   SD_Max_Height_Per_Event = col_double(),
                   n_Inund_Phase_A = col_integer(),
                   n_Inund_Phase_B = col_integer(),
                   n_Inund_Phase_C = col_integer(),
                   Hr_Inund_Phase_A = col_double(),
                   Hr_Inund_Phase_B = col_double(),
                   Hr_Inund_Phase_C = col_double())

inund.2 <- read_csv(file = "data/inund_results.csv",
                    col_types = inund.cols)

```



Visualizing the difference in hatching success between inundated and un-inundated nests: 

```{r}
inund.2 %>% filter(n_Inundation == 0) -> zero.inund
inund.2 %>% filter(n_Inundation > 0) -> only.inund

ggplot(data = zero.inund) + 
  geom_histogram(aes(x = prop_success),
                 bins = 10) +
    facet_grid(rows = vars(Season), cols = vars(Sector)) +
  labs(title = "No inundation", x = "Proportion of success")

# ggsave(filename = "figures/P_success_No_inundation.png",
#        device = "png", dpi = 600)
```

```{r}
ggplot(data = only.inund) + 
  geom_histogram(aes(x = prop_success),
                 bins = 10) +
  facet_grid(rows = vars(Season), cols = vars(Sector)) +
  labs(title = "Inundation", x = "Proportion of success")

# ggsave(filename = "figures/P_success_inundation.png",
#        device = "png", dpi = 600)

```

Not all sectors were monitored over the two seasons...  


Seems like disproportionate number of nests had zero hatching success when inundated. 

Look at correlation among some variables in inundated data

```{r}

only.inund %>% select(Nest_Elevation, Berm_Dist, Season, Sector, Northings, Eastings,
                      Hatched, Live_hatchlings, Total_clutch, prop_success,
                      Max_Height, n_Inundation, Max_Inund_Duration_Hr,
                      Total_Inund_Duration_Hr, Mean_Inund_Duration_Hr, 
                      Prop_Inund_Duration, SD_Inund_Duration_Hr, Mean_Max_Height_Per_Event,
                      SD_Max_Height_Per_Event, n_Inund_Phase_A, n_Inund_Phase_B,
                      n_Inund_Phase_C, Hr_Inund_Phase_A, Hr_Inund_Phase_B, Hr_Inund_Phase_C) %>%
  mutate(p_success = (Hatched + Live_hatchlings)/Total_clutch,
         f_Season = as.factor(Season),
         f_Sector = as.factor(Sector),
         Hr_Inund_Phase_AB = Hr_Inund_Phase_A + Hr_Inund_Phase_B,
         Hr_Inund_Phase_AC = Hr_Inund_Phase_A + Hr_Inund_Phase_C,
         Hr_Inund_Phase_BC = Hr_Inund_Phase_B + Hr_Inund_Phase_C) %>% 
  
  na.omit() -> only.inund.2

only.inund.2 %>% select(p_success, Max_Height, 
                        n_Inundation, Max_Inund_Duration_Hr,
                        Total_Inund_Duration_Hr, Mean_Inund_Duration_Hr,
                        Prop_Inund_Duration, SD_Inund_Duration_Hr, Mean_Max_Height_Per_Event,
                        SD_Max_Height_Per_Event, n_Inund_Phase_A, n_Inund_Phase_B,
                        n_Inund_Phase_C, Hr_Inund_Phase_A, Hr_Inund_Phase_B, Hr_Inund_Phase_C,
                        Hr_Inund_Phase_AB, Hr_Inund_Phase_AC, Hr_Inund_Phase_BC) %>%
  na.omit() -> only.inund.3

cormat <- cor(only.inund.3)

melted.cormat <- reshape2::melt(cormat)

ggplot(data = melted.cormat ) + 
  geom_tile(aes(x=Var1, y=Var2, fill=value)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 9, hjust = 1))


```

Can we predict hatching success using these predictors? Random Forest

Throw in all variables

```{r, echo=FALSE, results='hide'}
response <- only.inund.2$p_success

predictors <- only.inund.2 %>% select(-c(p_success, f_Season, Season, f_Sector, Sector))
RF.data <- as.data.frame(scale(predictors))

# Transform the proportion using asin (sqrt (p))
RF.data$p_success <- asin(sqrt(response))
RF.data$RV <- runif(nrow(RF.data), 0, 1)

ntree <- 500

M.3 <- as.formula("p_success ~ Nest_Elevation + 
                  Berm_Dist + 
                  Northings + 
                  Eastings +
                  Max_Height + 
                  n_Inundation + 
                  Max_Inund_Duration_Hr +
                  Total_Inund_Duration_Hr + 
                  Mean_Inund_Duration_Hr +
                  Prop_Inund_Duration + 
                  SD_Inund_Duration_Hr +
                  Mean_Max_Height_Per_Event +
                  SD_Max_Height_Per_Event +
                  n_Inund_Phase_A +
                  n_Inund_Phase_B +
                  n_Inund_Phase_C +
                  Hr_Inund_Phase_A +
                  Hr_Inund_Phase_B +
                  Hr_Inund_Phase_C +
                  Hr_Inund_Phase_AB +
                  Hr_Inund_Phase_AC +
                  Hr_Inund_Phase_BC +
                  RV")

RF.M.3 <- cforest(formula = M.3,
                  data = RF.data,
                  control = cforest_unbiased(ntree = ntree,
                                             trace = 500))
if (save.file)
  saveRDS(RF.M.3, file = "RData/RF_M_3_out.rds")

var.imp <- sort(varimp(RF.M.3), decreasing = FALSE)

if (save.file)
  saveRDS(var.imp, file = "RData/RF_M_3_varImp.rds")

pred.RF.M.3 <- RF.M.3@predict_response()

```


Look at the variable importance:
```{r}
var.imp.df <- data.frame(var.imp)
var.imp.df$Variable <- rownames(var.imp.df)

ggplot(data = var.imp.df) + 
  geom_point(aes(x = var.imp, y = reorder(Variable, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))
```

They seem to affect hatching success somewhat. Interesting to find that Phase B (18-36 days of incubation) affects more than other phases. 

```{r}
# back transform asin(sqrt(x))  
RF.data$p.success.prediction <- pred.RF.M.3
ggplot(data = RF.data) +
  geom_point(aes(x = (sin(p_success))^2, y = (sin(p.success.prediction))^2)) + 
  geom_abline(slope = 1.0, intercept = 0.0) + 
  ylim(c(0, 1)) + 
  labs(x = "Observed success rate", 
       y = "Predicted success rate")

```

Can't predict well... This is disappointing... 

How about zero_inund data:

Throw in all variables

```{r, echo=FALSE, results='hide'}
zero.inund %>% select(Nest_Elevation, Berm_Dist, Season, Sector, Northings, Eastings,
                      Hatched, Live_hatchlings, Total_clutch, prop_success) %>%
  mutate(p_success = (Hatched + Live_hatchlings)/Total_clutch,
         f_Season = as.factor(Season),
         f_Sector = as.factor(Sector)) %>% 
  
  na.omit() -> zero.inund.2
# p_success > 1 in one case... 
#response <- zero.inund.2$p_success
response <- zero.inund.2$prop_success/100

predictors <- zero.inund.2 %>% select(-c(p_success, f_Season, Season, f_Sector, Sector))
RF.data.zero.inund <- as.data.frame(scale(predictors))

RF.data.zero.inund$p_success <- asin(sqrt(response))
RF.data.zero.inund$RV <- runif(nrow(RF.data.zero.inund), 0, 1)

# ntree <- 500
# 
M.4 <- as.formula("p_success ~ Nest_Elevation +
                  Berm_Dist + Northings + Eastings +
                  RV")

RF.M.4.zero.inund <- cforest(formula = M.4,
                             data = RF.data.zero.inund,
                             control = cforest_unbiased(ntree = ntree,
                                             trace = 500))
if (save.file)
  saveRDS(RF.M.4, file = "RData/RF_M_4_zero_inund.out.rds")

var.imp.zero.inund <- sort(varimp(RF.M.4.zero.inund), decreasing = FALSE)

if (save.file)
  saveRDS(var.imp.zero.inund, file = "RData/RF_M_4_zero_inund_varImp.rds")

pred.RF.M.4.zero.inund <- RF.M.4.zero.inund@predict_response()

```


Look at the variable importance:
```{r}
var.imp.zero.inund.df <- data.frame(var.imp.zero.inund)
var.imp.zero.inund.df$Variable <- rownames(var.imp.zero.inund.df)

ggplot(data = var.imp.zero.inund.df) + 
  geom_point(aes(x = var.imp.zero.inund, y = reorder(Variable, var.imp.zero.inund)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))
```



```{r}
RF.data.zero.inund$p.success.prediction <- pred.RF.M.4.zero.inund
ggplot(data = RF.data.zero.inund) +
  geom_point(aes(x = (sin(p_success))^2, y = (sin(p.success.prediction))^2)) + 
  geom_abline(slope = 1.0, intercept = 0.0) + 
  ylim(c(0, 1)) + 
  labs(x = "Observed success rate", 
       y = "Predicted success rate")

```



Try beta regression (betareg)

```{r}

betareg.data <- RF.data
betareg.data$p.success.2 <- RF.data$p_success

# 0 < 0 < 1
# so, change zeros and 1s 
betareg.data$p.success.2[betareg.data$p_success > 0.999] <- 0.999
betareg.data$p.success.2[betareg.data$p_success < 0.001] <- 0.001
betareg.data$f_Season <- only.inund.2$f_Season
#betareg.data$f_Sector <- only.inund.2$f_Sector

# Use the variables that were considered important in RF
fit.betareg.1 <- betareg(p.success.2 ~ Berm_Dist + Max_Height + Mean_Max_Height_Per_Event + Hr_Inund_Phase_B +  Nest_Elevation + f_Season,
                         data = betareg.data)

summary(fit.betareg.1)
```

Including more predictors doesn't help tune the model. So, drop one at a time. Season was not useful at all... 

```{r}
fit.betareg.2 <- update(fit.betareg.1, .~. -f_Season)

summary(fit.betareg.2)
```

I don't like looking at these p values... When do we call a variable not important?

Let's try doing this in the Bayesian regression.

```{r}
response <- only.inund.2$p_success
# get rid of non-numeric variables
predictors <- only.inund.2 %>% select(-c(p_success, f_Season, Season, f_Sector, Sector))
Bayes.data <- as.data.frame(scale(predictors))
#Bayes.data$Season <- ifelse(only.inund.2$f_Season == "17/18", 0, 1)

jags.data <- list(y = response,
                  X1 = Bayes.data$Max_Height,
                  X2 = Bayes.data$Mean_Max_Height_Per_Event,
                  X3 = Bayes.data$Hr_Inund_Phase_B,
                  X4 = Bayes.data$Berm_Dist,
                  X5 = Bayes.data$Nest_Elevation,
                  N = nrow(Bayes.data),
                  n.pred = 5)

MCMC.params$model.file = "models/Model_logit_hatching.txt"

parameters <- c("b0", "b",
                "sigma.y", "loglik", "deviance")

jm.V5 <- jags(data = jags.data,
             #inits = inits,
             parameters.to.save= parameters,
             model.file = MCMC.params$model.file,
             n.chains = MCMC.params$n.chains,
             n.burnin = MCMC.params$n.burnin,
             n.thin = MCMC.params$n.thin,
             n.iter = MCMC.params$n.samples,
             DIC = T, 
             parallel=T)


jm.V5
```


Berm_Dist has the smallest f value. so let's remove it...
```{r}
jags.data <- list(y = response,
                  X1 = Bayes.data$Max_Height,
                  X2 = Bayes.data$Mean_Max_Height_Per_Event,
                  X3 = Bayes.data$Hr_Inund_Phase_B,
                  X4 = Bayes.data$Nest_Elevation,
                  N = nrow(Bayes.data),
                  n.pred = 4)

jm.V4 <- jags(data = jags.data,
             #inits = inits,
             parameters.to.save= parameters,
             model.file = MCMC.params$model.file,
             n.chains = MCMC.params$n.chains,
             n.burnin = MCMC.params$n.burnin,
             n.thin = MCMC.params$n.thin,
             n.iter = MCMC.params$n.samples,
             DIC = T, 
             parallel=T)

jm.V4

```

Berm_Dist is the lowest so remove. 

```{r}
jags.data <- list(y = response,
                  X1 = Bayes.data$Max_Height,
                  X2 = Bayes.data$Mean_Max_Height_Per_Event,
                  X3 = Bayes.data$Hr_Inund_Phase_B,
                  N = nrow(Bayes.data),
                  n.pred = 3)

jm.V3 <- jags(data = jags.data,
             #inits = inits,
             parameters.to.save= parameters,
             model.file = MCMC.params$model.file,
             n.chains = MCMC.params$n.chains,
             n.burnin = MCMC.params$n.burnin,
             n.thin = MCMC.params$n.thin,
             n.iter = MCMC.params$n.samples,
             DIC = T, 
             parallel=T)

jm.V3

```

```{r}
c(jm.V5$DIC, jm.V4$DIC, jm.V3$DIC)
```

The differences among the models are small. 

Look at LOOIC also

```{r}
n.params <- c(5, 4, 3)
models <- c("V5", "V4", "V3")
loo.out <- vector(mode = "list", length = length(n.params))
model.out <- list(jm.V5, jm.V4, jm.V3)
DIC <- LOOIC <- vector(mode = "numeric", length = length(n.params))
for (k in 1:length(n.params)){
  loo.out[[k]] <- compute.LOOIC(loglik = model.out[[k]]$sims.list$loglik,
                                data.vector = jags.data$y,
                                MCMC.params = MCMC.params)
  DIC[k] <- model.out[[k]]$DIC
  LOOIC[k] <- loo.out[[k]]$loo.out$estimates["looic","Estimate"] 
}

LOOIC_DIC <- data.frame(Model = models,
                        dDIC = DIC - min(DIC),
                        dLOOIC = LOOIC - min(LOOIC)) %>% arrange(by = dLOOIC)
LOOIC_DIC
#plot(loo.out$loo.out)
```

They are not that different. PSIS plots

```{r}
plot(loo.out[[1]]$loo.out)
```



```{r}
plot(loo.out[[2]]$loo.out)
```

```{r}
plot(loo.out[[3]]$loo.out)
```


Not bad... I see a couple of outliers. Let's take a look at those two.

```{r}
psis.3 <- loo.out[[3]]$loo.out$pointwise

high.psis <- psis.3 %>% 
  as.data.frame() %>% rownames_to_column("row_ID") %>%
  filter(influence_pareto_k > 0.5)

data.high.psis <- only.inund.2[high.psis$row_ID,]

data.high.psis

```

These are two extreme (not the most extreme) cases with low and high hatching success rates.

These models are pretty much the same. So, I'll just pick the simplest model with 3 variables: Max_Height, Mean_Max_Height_Per_Event, and Hr_Inund_Phase_B. 

```{r}
jm.V3$summary %>% as.data.frame %>% rownames_to_column("parameter") -> tmp

tmp[grep("b", tmp$parameter),] %>% 
  select(-c('25%', '75%', overlap0, f, Rhat, n.eff)) -> tmp2

tmp2

```

b[1] (Max_Height) > 0; A positive relationship between Max_Height and p_success
b[2] (Mean_Max_Height_Per_Event) < 0; A negative relationship between Mean_Max_Height_Per_Event and p_success
b[3] (Hr_Inund_Phase_B) < 0; A negative relationship between Hr_Inund_Phase_B and p_success

Smaller maximum tide height of inundation events, greater mean maximum tide height per event, and longer inundation during Phase B (18-36 days) result in low hatching success rate. 

Does this make sense...?

```{r}
bayesplot::mcmc_trace(jm.V5$samples, c("b0", "b[1]", "b[2]", "b[3]"))
```

Not great trace plots, except the intercept... 

```{r}
bayesplot::mcmc_dens(jm.V5$samples, c("b0", "b[1]", "b[2]", "b[3]"))
```

Try to compute Bayesian R2 values... Gelman et al. (2018)

```{r}
y <- response    # observed data
X <- Bayes.data %>% 
  select(Max_Height, Mean_Max_Height_Per_Event, Hr_Inund_Phase_B) %>% 
  as.matrix() 

# Data matrix
X <- cbind(1, X)

# need to get posterior samples
varname <- c("b0", "b[1]", "b[2]", "b[3]")
betas <- do.call(rbind, jm.V3$samples[, varname])

R2.V3 <- bayes.logit.R2(X, betas, jm.V3$samples, "sigma.y")

ggplot(data = data.frame(R2 = R2.V3)) +
  geom_histogram(aes(x = R2), bins = 20)

```

R2 ~ 0.4... not great but not too bad either... 

