---
title: "R Notebook"
output: html_notebook
---

This document follows Inundation_hatchsuccess_v1.Rmd. Data were extracted in the previous step. In this analysis, I sue Random Forest to predict hatching success. 

```{r}
# clear the workspace and bring in libraries
rm(list=ls())
library(tidyverse)
library(party)
library(betareg)
library(jagsUI)
library(bayesplot)
library(loo)

source("Dunstan_Inundation_fcns.R")

save.fig <- F
save.file <- F

MCMC.params <- list(n.samples = 50000,
                    n.burnin = 45000,
                    n.thin = 5,
                    n.chains = 5)

```



```{r}
inund.cols <- cols(fid = col_integer(),
                   Nest_UID = col_character(),
                   Northings = col_double(),
                   Eastings = col_double(),
                   Nest_Elevation = col_double(),
                   Berm_Dist = col_double(),
                   Habitat = col_character(),
                   Sector = col_character(),
                   Island_Aspect = col_character(),
                   ID_closest_logger = col_character(),
                   Season = col_character(),
                   Survey = col_character(),
                   Incubation_Start = col_date(format = "%Y-%m-%d"),
                   Incubation_Finish = col_date(format = "%Y-%m-%d"),
                   Date_dug = col_date(format = "%Y-%m-%d"),
                   Hatched = col_integer(),
                   Live_hatchlings = col_integer(),
                   Dead_hatchlings = col_integer(),
                   Phase_1 = col_integer(),
                   Phase_2 = col_integer(),
                   Phase_3 = col_integer(),
                   Phase_4 = col_integer(),
                   Phase_5 = col_integer(),
                   Phase_6 = col_integer(),
                   Decomposed = col_integer(),
                   Total_unhatched = col_integer(),
                   Total_clutch = col_integer(),
                   prop_success = col_double(),
                   sector = col_character(),
                   season = col_character(),
                   Max_Height = col_double(),
                   n_Inundation = col_integer(),
                   Max_Inund_Duration_Hr = col_double(),
                   Total_Inund_Duration_Hr = col_double(),
                   Mean_Inund_Duration_Hr = col_double(),
                   Prop_Inund_Duration = col_double(),
                   SD_Inund_Duration_Hr = col_double(),
                   Mean_Max_Height_Per_Event = col_double(),
                   SD_Max_Height_Per_Event = col_double(),
                   n_Inund_Phase_A = col_integer(),
                   n_Inund_Phase_B = col_integer(),
                   n_Inund_Phase_C = col_integer(),
                   Hr_Inund_Phase_A = col_double(),
                   Hr_Inund_Phase_B = col_double(),
                   Hr_Inund_Phase_C = col_double(),
                   inund_hrs_lt_25 = col_double(),
                   inund_hrs_gt_25_lt_50 = col_double(), 
                   inund_hrs_gt_50_lt_75 = col_double(),
                   inund_hrs_gt_75 = col_double())

inund.1 <- read_csv(file = "data/inund_results.csv",
                    col_types = inund.cols)

# remove four nests whose bottom height was above the nearest logger the entire duration.

inund.1 %>% filter(!Nest_UID %in% c("1812-081", "1812-003", "1802-18", "1712-076")) -> inund.2
```



Visualizing the difference in hatching success between inundated and un-inundated nests: 

```{r}
inund.2 %>% filter(n_Inundation == 0) -> zero.inund
inund.2 %>% filter(n_Inundation > 0) -> only.inund

ggplot(data = zero.inund) + 
  geom_histogram(aes(x = prop_success),
                 bins = 10) +
    facet_grid(rows = vars(Season), cols = vars(Sector)) +
  labs(title = "No inundation", x = "Proportion of success")

# ggsave(filename = "figures/P_success_No_inundation.png",
#        device = "png", dpi = 600)
```

```{r}
ggplot(data = only.inund) + 
  geom_histogram(aes(x = prop_success),
                 bins = 10) +
  facet_grid(rows = vars(Season), cols = vars(Sector)) +
  labs(title = "Inundation", x = "Proportion of success")

# ggsave(filename = "figures/P_success_inundation.png",
#        device = "png", dpi = 600)

```

Not all sectors were monitored over the two seasons...  


Seems like disproportionate number of nests had zero hatching success when inundated. 

Look at correlation among some variables in inundated data

```{r}

only.inund %>% select(Nest_Elevation, Berm_Dist, Season, Sector, Northings, Eastings,
                      Hatched, Live_hatchlings, Total_clutch, prop_success,
                      Max_Height, n_Inundation, Max_Inund_Duration_Hr,
                      Total_Inund_Duration_Hr, Mean_Inund_Duration_Hr, 
                      Prop_Inund_Duration, SD_Inund_Duration_Hr, Mean_Max_Height_Per_Event,
                      SD_Max_Height_Per_Event, n_Inund_Phase_A, n_Inund_Phase_B,
                      n_Inund_Phase_C, Hr_Inund_Phase_A, Hr_Inund_Phase_B, Hr_Inund_Phase_C,
                      inund_hrs_lt_25, inund_hrs_gt_25_lt_50, inund_hrs_gt_50_lt_75,
                      inund_hrs_gt_75) %>%
  mutate(p_success = (Hatched + Live_hatchlings)/Total_clutch,
         f_Season = as.factor(Season),
         f_Sector = as.factor(Sector),
         Hr_Inund_Phase_AB = Hr_Inund_Phase_A + Hr_Inund_Phase_B,
         Hr_Inund_Phase_AC = Hr_Inund_Phase_A + Hr_Inund_Phase_C,
         Hr_Inund_Phase_BC = Hr_Inund_Phase_B + Hr_Inund_Phase_C) %>% 
  
  na.omit() -> only.inund.2

only.inund.2 %>% select(p_success, Max_Height, 
                        n_Inundation, Max_Inund_Duration_Hr,
                        Total_Inund_Duration_Hr, Mean_Inund_Duration_Hr,
                        Prop_Inund_Duration, SD_Inund_Duration_Hr, Mean_Max_Height_Per_Event,
                        SD_Max_Height_Per_Event, n_Inund_Phase_A, n_Inund_Phase_B,
                        n_Inund_Phase_C, Hr_Inund_Phase_A, Hr_Inund_Phase_B, Hr_Inund_Phase_C,
                        Hr_Inund_Phase_AB, Hr_Inund_Phase_AC, Hr_Inund_Phase_BC,
                        inund_hrs_lt_25, inund_hrs_gt_25_lt_50, inund_hrs_gt_50_lt_75,
                        inund_hrs_gt_75) %>%
  na.omit() -> only.inund.3

cormat <- cor(only.inund.3)

melted.cormat <- reshape2::melt(cormat)

ggplot(data = melted.cormat ) + 
  geom_tile(aes(x=Var1, y=Var2, fill=value)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 9, hjust = 1))


```

Can we predict hatching success using these predictors? Random Forest

Throw in all variables

```{r, echo=FALSE, results='hide'}
response <- only.inund.2$prop_success/100

predictors <- only.inund.2 %>% select(-c(p_success, prop_success, f_Season, Season, f_Sector, Sector))
#RF.data <- as.data.frame(predictors)
RF.data <- as.data.frame(scale(predictors))

# Transform the proportion using asin (sqrt (p)) - may not be necessary...
#RF.data$p_success <- asin(sqrt(response))

RF.data$p_success <- response

RF.data$RV <- runif(nrow(RF.data), 0, 1)

ntree <- 500

M.3 <- as.formula("p_success ~ Nest_Elevation + 
                  Berm_Dist + 
                  Northings + 
                  Eastings +
                  Max_Height + 
                  n_Inundation + 
                  Max_Inund_Duration_Hr +
                  Total_Inund_Duration_Hr + 
                  Mean_Inund_Duration_Hr +
                  Prop_Inund_Duration + 
                  SD_Inund_Duration_Hr +
                  Mean_Max_Height_Per_Event +
                  SD_Max_Height_Per_Event +
                  n_Inund_Phase_A +
                  n_Inund_Phase_B +
                  n_Inund_Phase_C +
                  Hr_Inund_Phase_A +
                  Hr_Inund_Phase_B +
                  Hr_Inund_Phase_C +
                  Hr_Inund_Phase_AB +
                  Hr_Inund_Phase_AC +
                  Hr_Inund_Phase_BC +
                  inund_hrs_lt_25 + 
                  inund_hrs_gt_25_lt_50 + 
                  inund_hrs_gt_50_lt_75 +
                  inund_hrs_gt_75 +
                  RV")

RF.M.3 <- cforest(formula = M.3,
                  data = RF.data,
                  control = cforest_unbiased(ntree = ntree,
                                             trace = 500))
if (save.file)
  saveRDS(RF.M.3, file = "RData/RF_M_3_out.rds")

var.imp <- sort(varimp(RF.M.3), decreasing = FALSE)

if (save.file)
  saveRDS(var.imp, file = "RData/RF_M_3_varImp.rds")

pred.RF.M.3 <- RF.M.3@predict_response()

```


Look at the variable importance:
```{r}
var.imp.df <- data.frame(var.imp)
var.imp.df$Variable <- rownames(var.imp.df)

ggplot(data = var.imp.df) + 
  geom_point(aes(x = var.imp, y = reorder(Variable, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))
```


```{r}
# back transform asin(sqrt(x))  
RF.data$p.success.prediction <- pred.RF.M.3
ggplot(data = RF.data) +
  #geom_point(aes(x = (sin(p_success))^2, y = (sin(p.success.prediction))^2)) + 
  geom_point(aes(x = p_success, y = p.success.prediction)) + 
  geom_abline(slope = 1.0, intercept = 0.0) + 
  ylim(c(0, 1)) + 
  labs(x = "Observed success rate", 
       y = "Predicted success rate")

```


Pull out the top 7 variables and also add some interactions.

```{r}
only.inund.2 %>% select(Berm_Dist, Max_Height, Hr_Inund_Phase_AB, Mean_Max_Height_Per_Event,
                   Nest_Elevation, Hr_Inund_Phase_B, n_Inund_Phase_B) %>%
  mutate(Mean_Max_Height_Berm_Dist = Berm_Dist * Mean_Max_Height_Per_Event,
         Max_Height_Berm_Dist = Berm_Dist * Max_Height) %>% 
  scale() %>%
  as.data.frame()  -> RF.data.2

# Transform the proportion using asin (sqrt (p))
#RF.data.2$p_success <- asin(sqrt(only.inund.2$prop_success/100))
RF.data.2$p_success <- response
RF.data.2$RV <- runif(nrow(RF.data.2), 0, 1)

ntree <- 500

M.5 <- as.formula("p_success ~ Berm_Dist + 
                  Max_Height + 
                  Hr_Inund_Phase_AB + 
                  Mean_Max_Height_Per_Event +
                  Nest_Elevation + 
                  Hr_Inund_Phase_B + 
                  n_Inund_Phase_B +
                  Mean_Max_Height_Berm_Dist +
                  Max_Height_Berm_Dist+
                  RV")

RF.M.5 <- cforest(formula = M.5,
                  data = RF.data.2,
                  control = cforest_unbiased(ntree = ntree,
                                             trace = 500))


var.imp <- sort(varimp(RF.M.5), decreasing = FALSE)

if (save.file)
  saveRDS(var.imp, file = "RData/RF_M_5_varImp.rds")

pred.RF.M.5 <- RF.M.5@predict_response()

```



Look at the variable importance:

```{r}
var.imp.df <- data.frame(var.imp)
var.imp.df$Variable <- rownames(var.imp.df)

ggplot(data = var.imp.df) + 
  geom_point(aes(x = var.imp, y = reorder(Variable, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))
```


They seem to affect hatching success somewhat. Interesting to find that Phase B (18-36 days of incubation) affects more than other phases. 

```{r}
# back transform asin(sqrt(x))  
RF.data$p.success.prediction <- pred.RF.M.5
ggplot(data = RF.data) +
  #geom_point(aes(x = (sin(p_success))^2, y = (sin(p.success.prediction))^2)) + 
  geom_point(aes(x = p_success, y = p.success.prediction)) + 
  geom_abline(slope = 1.0, intercept = 0.0) + 
  ylim(c(0, 1)) + 
  labs(x = "Observed success rate", 
       y = "Predicted success rate")

```

Can't predict well... This is disappointing... 

How about zero_inund data:

Throw in all variables

```{r, echo=FALSE, results='hide'}
zero.inund %>% select(Nest_Elevation, Berm_Dist, Season, 
                      Sector, Northings, Eastings,
                      Hatched, Live_hatchlings, 
                      Total_clutch, prop_success) %>%
  mutate(p_success = prop_success/100,
         f_Season = as.factor(Season),
         f_Sector = as.factor(Sector)) %>% 
  
  na.omit() -> zero.inund.2
# p_success > 1 in one case... 
response <- zero.inund.2$p_success
#response <- zero.inund.2$prop_success/100

predictors <- zero.inund.2 %>% select(-c(p_success, f_Season, 
                                         Season, f_Sector, Sector))
RF.data.zero.inund <- as.data.frame(scale(predictors))

#RF.data.zero.inund$p_success <- asin(sqrt(response))
RF.data.zero.inund$p_success <- response
RF.data.zero.inund$RV <- runif(nrow(RF.data.zero.inund), 0, 1)

# ntree <- 500
# 
M.4 <- as.formula("p_success ~ Nest_Elevation +
                  Berm_Dist + Northings + Eastings + 
                  RV")

RF.M.4.zero.inund <- cforest(formula = M.4,
                             data = RF.data.zero.inund,
                             control = cforest_unbiased(ntree = ntree,
                                                        trace = 500))
if (save.file)
  saveRDS(RF.M.4, file = "RData/RF_M_4_zero_inund.out.rds")

var.imp.zero.inund <- sort(varimp(RF.M.4.zero.inund), decreasing = FALSE)

if (save.file)
  saveRDS(var.imp.zero.inund, file = "RData/RF_M_4_zero_inund_varImp.rds")

pred.RF.M.4.zero.inund <- RF.M.4.zero.inund@predict_response()

```


Look at the variable importance:
```{r}
var.imp.zero.inund.df <- data.frame(var.imp.zero.inund)
var.imp.zero.inund.df$Variable <- rownames(var.imp.zero.inund.df)

ggplot(data = var.imp.zero.inund.df) + 
  geom_point(aes(x = var.imp.zero.inund, y = reorder(Variable, var.imp.zero.inund)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))
```


```{r}
RF.data.zero.inund$p.success.prediction <- pred.RF.M.4.zero.inund
ggplot(data = RF.data.zero.inund) +
  #geom_point(aes(x = (sin(p_success))^2, y = (sin(p.success.prediction))^2)) + 
  geom_point(aes(x = p_success, y = p.success.prediction)) + 
  geom_abline(slope = 1.0, intercept = 0.0) + 
  ylim(c(0, 1)) + 
  labs(x = "Observed success rate", 
       y = "Predicted success rate")

```



Try beta regression (betareg)

```{r}

betareg.data <- RF.data
betareg.data$p.success.2 <- RF.data$p_success

# 0 < 0 < 1
# so, change zeros and 1s 
betareg.data$p.success.2[betareg.data$p_success > 0.999] <- 0.999
betareg.data$p.success.2[betareg.data$p_success < 0.001] <- 0.001
betareg.data$f_Season <- only.inund.2$f_Season
#betareg.data$f_Sector <- only.inund.2$f_Sector

# Use the variables that were considered important in RF
fit.betareg.1 <- betareg(p.success.2 ~ Berm_Dist + Max_Height + Mean_Max_Height_Per_Event + Hr_Inund_Phase_B +  Nest_Elevation + f_Season,
                         data = betareg.data)

summary(fit.betareg.1)
```

Including more predictors doesn't help tune the model. So, drop one at a time. Season was not useful at all... 

```{r}
fit.betareg.2 <- update(fit.betareg.1, .~. -f_Season)

summary(fit.betareg.2)
```

I don't like looking at these p values... When do we call a variable not important?

Let's try doing this in the Bayesian regression.

```{r}
response <- only.inund.2$p_success
# get rid of non-numeric variables
predictors <- only.inund.2 %>% select(-c(p_success, f_Season, Season, f_Sector, Sector))
Bayes.data <- as.data.frame(scale(predictors))
#Bayes.data$Season <- ifelse(only.inund.2$f_Season == "17/18", 0, 1)

jags.data <- list(y = response,
                  X = cbind(1, Bayes.data$Max_Height,
                            Bayes.data$Mean_Max_Height_Per_Event,
                            Bayes.data$Hr_Inund_Phase_B,
                            Bayes.data$Berm_Dist,
                            Bayes.data$Nest_Elevation),
                  N = nrow(Bayes.data),
                  n.pred = 5)

MCMC.params$model.file = "models/Model_logit_hatching.txt"

parameters <- c("b",
                "sigma.y", "loglik", "deviance")

jm.V5 <- jags(data = jags.data,
             #inits = inits,
             parameters.to.save= parameters,
             model.file = MCMC.params$model.file,
             n.chains = MCMC.params$n.chains,
             n.burnin = MCMC.params$n.burnin,
             n.thin = MCMC.params$n.thin,
             n.iter = MCMC.params$n.samples,
             DIC = T, 
             parallel=T)


# need to get posterior samples
varname <- c("b[1]", "b[2]", "b[3]", "b[4]", "b[5]", "b[6]")
betas <- do.call(rbind, jm.V5$samples[, varname])

R2.V5 <- bayes.logit.R2(jags.data$X, betas, jm.V5$samples, "sigma.y")

jm.V5
```


b[6] has the smallest f value. so let's remove it...

```{r}
jags.data <- list(y = response, #asin(sqrt(response)),
                  X = cbind(1, Bayes.data$Max_Height,
                            Bayes.data$Mean_Max_Height_Per_Event,
                            Bayes.data$Hr_Inund_Phase_B,
                            Bayes.data$Berm_Dist),
                  N = nrow(Bayes.data),
                  n.pred = 4)

jm.V4 <- jags(data = jags.data,
             #inits = inits,
             parameters.to.save= parameters,
             model.file = MCMC.params$model.file,
             n.chains = MCMC.params$n.chains,
             n.burnin = MCMC.params$n.burnin,
             n.thin = MCMC.params$n.thin,
             n.iter = MCMC.params$n.samples,
             DIC = T, 
             parallel=T)


# need to get posterior samples
varname <- c("b[1]", "b[2]", "b[3]", "b[4]", "b[5]")
betas <- do.call(rbind, jm.V4$samples[, varname])

R2.V4 <- bayes.logit.R2(jags.data$X, betas, jm.V4$samples, "sigma.y")

jm.V4

```

b[4] is the lowest so remove. 

```{r}
jags.data <- list(y = response, #asin(sqrt(response)),
                  X = cbind(1, Bayes.data$Max_Height,
                            Bayes.data$Mean_Max_Height_Per_Event,
                            Bayes.data$Berm_Dist),
                  N = nrow(Bayes.data),
                  n.pred = 3)

jm.V3 <- jags(data = jags.data,
             #inits = inits,
             parameters.to.save= parameters,
             model.file = MCMC.params$model.file,
             n.chains = MCMC.params$n.chains,
             n.burnin = MCMC.params$n.burnin,
             n.thin = MCMC.params$n.thin,
             n.iter = MCMC.params$n.samples,
             DIC = T, 
             parallel=T)


# need to get posterior samples
varname <- c("b[1]", "b[2]", "b[3]", "b[4]")
betas <- do.call(rbind, jm.V3$samples[, varname])

R2.V3 <- bayes.logit.R2(jags.data$X, betas, jm.V3$samples, "sigma.y")

jm.V3

```

Could there be interactions...?

```{r}
predictors <- only.inund.2 %>% select(-c(p_success, f_Season, Season, f_Sector, Sector))
predictors %>% mutate(Max_Height_Berm_Dist = Max_Height * Berm_Dist,
                      Mean_Max_Height_Berm_Dist = Mean_Max_Height_Per_Event * Berm_Dist) -> predictors

Bayes.data <- as.data.frame(scale(predictors))
#Bayes.data$Season <- ifelse(only.inund.2$f_Season == "17/18", 0, 1)

jags.data <- list(y = response,
                  X = cbind(1, Bayes.data$Max_Height,
                            Bayes.data$Mean_Max_Height_Per_Event,
                            Bayes.data$Berm_Dist,
                            Bayes.data$Max_Height_Berm_Dist,
                            Bayes.data$Mean_Max_Height_Berm_Dist),
                  N = nrow(Bayes.data),
                  n.pred = 5)

jm.V5.interactions <- jags(data = jags.data,
             #inits = inits,
             parameters.to.save= parameters,
             model.file = MCMC.params$model.file,
             n.chains = MCMC.params$n.chains,
             n.burnin = MCMC.params$n.burnin,
             n.thin = MCMC.params$n.thin,
             n.iter = MCMC.params$n.samples,
             DIC = T, 
             parallel=T)


# need to get posterior samples
varname <- c("b[1]", "b[2]", "b[3]", "b[4]", "b[5]", "b[6]")
betas <- do.call(rbind, jm.V5.interactions$samples[, varname])

R2.V5.interactions <- bayes.logit.R2(jags.data$X, betas, jm.V5.interactions$samples, "sigma.y")

jm.V5.interactions

```

Max_Height_Berm_Dist doesn't do too much so drop it.

```{r}
jags.data <- list(y = response,
                  X = cbind(1, Bayes.data$Max_Height,
                            Bayes.data$Mean_Max_Height_Per_Event,
                            Bayes.data$Berm_Dist,
                            Bayes.data$Mean_Max_Height_Berm_Dist),
                  N = nrow(Bayes.data),
                  n.pred = 4)

jm.V4.interactions <- jags(data = jags.data,
                           #inits = inits,
                           parameters.to.save= parameters,
                           model.file = MCMC.params$model.file,
                           n.chains = MCMC.params$n.chains,
                           n.burnin = MCMC.params$n.burnin,
                           n.thin = MCMC.params$n.thin,
                           n.iter = MCMC.params$n.samples,
                           DIC = T, 
                           parallel=T)


# need to get posterior samples
varname <- c("b[1]", "b[2]", "b[3]", "b[4]", "b[5]")
betas <- do.call(rbind, jm.V4.interactions$samples[, varname])

R2.V4.interactions <- bayes.logit.R2(jags.data$X, betas, jm.V4.interactions$samples, "sigma.y")

jm.V4.interactions
```





```{r}
c(jm.V5$DIC, jm.V4$DIC, jm.V3$DIC, jm.V5.interactions$DIC, jm.V4.interactions$DIC)
```

Look at LOOIC also

```{r}
n.params <- c(5, 4, 3, 5, 4)
models <- c("V5", "V4", "V3", "V5_interactions", "V4_interactions")
loo.out <- vector(mode = "list", length = length(n.params))
model.out <- list(jm.V5, jm.V4, jm.V3, jm.V5.interactions, jm.V4.interactions)
DIC <- LOOIC <- vector(mode = "numeric", length = length(n.params))
for (k in 1:length(n.params)){
  loo.out[[k]] <- compute.LOOIC(loglik = model.out[[k]]$sims.list$loglik,
                                data.vector = jags.data$y,
                                MCMC.params = MCMC.params)
  DIC[k] <- model.out[[k]]$DIC
  LOOIC[k] <- loo.out[[k]]$loo.out$estimates["looic","Estimate"] 
}

LOOIC_DIC <- data.frame(Model = models,
                        dDIC = DIC - min(DIC),
                        dLOOIC = LOOIC - min(LOOIC)) %>% arrange(by = dLOOIC)
LOOIC_DIC
#plot(loo.out$loo.out)
```

Ones with interactions seem to do better.   

They are not that different. PSIS plots

```{r}
plot(loo.out[[1]]$loo.out)
```



```{r}
plot(loo.out[[2]]$loo.out)
```

```{r}
plot(loo.out[[3]]$loo.out)
```


```{r}
plot(loo.out[[4]]$loo.out)
```



```{r}
plot(loo.out[[5]]$loo.out)
```

All these diagnostics point to V4.interactions as the best. 

<!-- Not bad... I see a couple of outliers. Let's take a look at those two. -->

```{r}
# psis.3 <- loo.out[[3]]$loo.out$pointwise
# 
# high.psis <- psis.3 %>% 
#   as.data.frame() %>% rownames_to_column("row_ID") %>%
#   filter(influence_pareto_k > 0.5)
# 
# data.high.psis <- only.inund.2[high.psis$row_ID,]
# 
# data.high.psis

```

<!-- These are two extreme (not the most extreme) cases with low and high hatching success rates. -->



<!-- These models are pretty much the same. So, I'll just pick the simplest model with 3 variables: Max_Height, Mean_Max_Height_Per_Event, and Hr_Inund_Phase_B.  -->

Max_Height,  Mean_Max_Height_Per_Event, Berm_Dist, Mean_Max_Height_Per_Event * Berm_Dist
                            
```{r}
jm.V4.interactions$summary %>% as.data.frame %>% rownames_to_column("parameter") -> tmp

tmp[grep("b", tmp$parameter),] %>% 
  select(-c('25%', '75%', overlap0, f, Rhat, n.eff)) -> tmp2

tmp2

```

b[2] (Max_Height) > 0; A positive relationship between Max_Height and p_success
b[3] (Mean_Max_Height_Per_Event) < 0; A negative relationship between Mean_Max_Height_Per_Event and p_success
b[4] (Berm_Dist) < 0; A negative relationship between Berm_Dist and p_success
b[5] (Mean_Max_Height_Per_Event x Berm_Dist) > 0; A positive relationship

Smaller maximum tide height of inundation events, greater mean maximum tide height per event, and greater distance from the berm result in low hatching success rate. How do I interpret the interaction term?

Does this make sense...?



```{r}
bayesplot::mcmc_trace(jm.V4.interactions$samples, c("b[1]", "b[2]", "b[3]", "b[4]", "b[5]"))
```

Not great trace plots, except the intercept... 

```{r}
bayesplot::mcmc_dens(jm.V4.interactions$samples, c("b[1]", "b[2]", "b[3]", "b[4]", "b[5]"))
```

Try to compute Bayesian R2 values... Gelman et al. (2018)

```{r}

ggplot(data = data.frame(R2 = R2.V4.interactions)) +
  geom_histogram(aes(x = R2), bins = 20)

```

R2 ~ 0.4... not great but not too bad either... 


transform y using asine(sqrt(y))

This turned out to be not useful at all...


<!-- ```{r} -->
<!-- jags.data <- list(y = asin(sqrt(response)), -->
<!--                   X = cbind(1, Bayes.data$Max_Height, -->
<!--                             Bayes.data$Mean_Max_Height_Per_Event, -->
<!--                             Bayes.data$Hr_Inund_Phase_B, -->
<!--                             Bayes.data$Berm_Dist, -->
<!--                             Bayes.data$Nest_Elevation), -->
<!--                   N = nrow(Bayes.data), -->
<!--                   n.pred = 5) -->

<!-- MCMC.params$model.file = "models/Model_linear_regression.txt" -->

<!-- parameters <- c("b", -->
<!--                 "sigma.y", "loglik", "deviance") -->

<!-- jm.asine.V5 <- jags(data = jags.data, -->
<!--              #inits = inits, -->
<!--              parameters.to.save= parameters, -->
<!--              model.file = MCMC.params$model.file, -->
<!--              n.chains = MCMC.params$n.chains, -->
<!--              n.burnin = MCMC.params$n.burnin, -->
<!--              n.thin = MCMC.params$n.thin, -->
<!--              n.iter = MCMC.params$n.samples, -->
<!--              DIC = T,  -->
<!--              parallel=T) -->


<!-- # need to get posterior samples -->
<!-- varname <- c("b[1]", "b[2]", "b[3]", "b[4]", "b[5]", "b[6]") -->
<!-- betas <- do.call(rbind, jm.asine.V5$samples[, varname]) -->

<!-- R2.asine.V5 <- bayes.logit.R2(jags.data$X, betas, jm.asine.V5$samples, "sigma.y") -->

<!-- jm.asine.V5 -->
<!-- ``` -->




<!-- ```{r} -->
<!-- jags.data <- list(y = asin(sqrt(response)), -->
<!--                   X = cbind(1, Bayes.data$Max_Height, -->
<!--                             Bayes.data$Mean_Max_Height_Per_Event, -->
<!--                             Bayes.data$Hr_Inund_Phase_B, -->
<!--                             Bayes.data$Berm_Dist), -->
<!--                   N = nrow(Bayes.data), -->
<!--                   n.pred = 4) -->

<!-- jm.asine.V4 <- jags(data = jags.data, -->
<!--              #inits = inits, -->
<!--              parameters.to.save= parameters, -->
<!--              model.file = MCMC.params$model.file, -->
<!--              n.chains = MCMC.params$n.chains, -->
<!--              n.burnin = MCMC.params$n.burnin, -->
<!--              n.thin = MCMC.params$n.thin, -->
<!--              n.iter = MCMC.params$n.samples, -->
<!--              DIC = T,  -->
<!--              parallel=T) -->


<!-- # need to get posterior samples -->
<!-- varname <- c("b[1]", "b[2]", "b[3]", "b[4]", "b[5]") -->
<!-- betas <- do.call(rbind, jm.asine.V4$samples[, varname]) -->

<!-- R2.asine.V4 <- bayes.logit.R2(jags.data$X, betas, jm.asine.V4$samples, "sigma.y") -->

<!-- jm.asine.V4 -->
<!-- ``` -->
