---
title: "R Notebook"
output: html_notebook
---

This document follows Inundation_hatchsuccess_v1.Rmd. Data were extracted in the previous step. In this analysis, I sue Random Forest to predict hatching success. 

```{r}
# clear the workspace and bring in libraries
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(readr)
library(lubridate)
library(party)

source("Dunstan_Inundation_fcns.R")
save.fig <- F
save.output <- F

```



```{r}
inund.cols <- cols(fid = col_integer(),
                   Nest_UID = col_character(),
                   Northings = col_double(),
                   Eastings = col_double(),
                   Nest_Elevation = col_double(),
                   Berm_Dist = col_double(),
                   Habitat = col_character(),
                   Sector = col_character(),
                   Island_Aspect = col_character(),
                   ID_closest_logger = col_character(),
                   Season = col_character(),
                   Survey = col_character(),
                   Incubation_Start = col_date(format = "%Y-%m-%d"),
                   Incubation_Finish = col_date(format = "%Y-%m-%d"),
                   Date_dug = col_date(format = "%Y-%m-%d"),
                   Hatched = col_integer(),
                   Live_hatchlings = col_integer(),
                   Dead_hatchlings = col_integer(),
                   Phase_1 = col_integer(),
                   Phase_2 = col_integer(),
                   Phase_3 = col_integer(),
                   Phase_4 = col_integer(),
                   Phase_5 = col_integer(),
                   Phase_6 = col_integer(),
                   Decomposed = col_integer(),
                   Total_unhatched = col_integer(),
                   Total_clutch = col_integer(),
                   prop_success = col_double(),
                   Max_Height = col_double(),
                   n_Inundation = col_integer(),
                   Max_Inund_Duration_Hr = col_double(),
                   Total_Inund_Duration_Hr = col_double(),
                   Mean_Inund_Duration_Hr = col_double(),
                   Prop_Inund_Duration = col_double(),
                   SD_Inund_Duration_Hr = col_double(),
                   Mean_Max_Height_Per_Event = col_double(),
                   SD_Max_Height_Per_Event = col_double(),
                   n_Inund_Phase_A = col_integer(),
                   n_Inund_Phase_B = col_integer(),
                   n_Inund_Phase_C = col_integer(),
                   Hr_Inund_Phase_A = col_double(),
                   Hr_Inund_Phase_B = col_double(),
                   Hr_Inund_Phase_C = col_double())

inund.2 <- read_csv(file = "data/inund_results.csv",
                    col_types = inund.cols)

```



Visualizing the difference in hatching success between inundated and un-inundated nests: 

```{r}
inund.2 %>% filter(n_Inundation == 0) -> zero.inund
inund.2 %>% filter(n_Inundation > 0) -> only.inund

ggplot(data = zero.inund) + 
  geom_histogram(aes(x = prop_success),
                 bins = 20) +
  labs(title = "No inundation", x = "Proportion of success")
```

```{r}
ggplot(data = only.inund) + 
  geom_histogram(aes(x = prop_success),
                 bins = 20) +
  labs(title = "Inundation", x = "Proportion of success")

```


Seems like disproportionate number of nests had zero hatching success when inundated. 

Look at correlation among some variables in inundated data

```{r}

only.inund %>% select(Nest_Elevation, Berm_Dist, Season,
                      Hatched, Live_hatchlings, Total_clutch, prop_success,
                      Max_Height, n_Inundation, Max_Inund_Duration_Hr,
                      Total_Inund_Duration_Hr, Mean_Inund_Duration_Hr, 
                      Prop_Inund_Duration, SD_Inund_Duration_Hr, Mean_Max_Height_Per_Event,
                      SD_Max_Height_Per_Event, n_Inund_Phase_A, n_Inund_Phase_B,
                      n_Inund_Phase_C, Hr_Inund_Phase_A, Hr_Inund_Phase_B, Hr_Inund_Phase_C) %>%
  mutate(p_success = (Hatched + Live_hatchlings)/Total_clutch,
         f_Season = as.factor(Season)) %>% 
  
  na.omit() -> only.inund.2

only.inund.2 %>% select(p_success, Max_Height, n_Inundation, Max_Inund_Duration_Hr,
                      Total_Inund_Duration_Hr, Mean_Inund_Duration_Hr,
                      Prop_Inund_Duration, SD_Inund_Duration_Hr, Mean_Max_Height_Per_Event,
                      SD_Max_Height_Per_Event, n_Inund_Phase_A, n_Inund_Phase_B,
                      n_Inund_Phase_C, Hr_Inund_Phase_A, Hr_Inund_Phase_B, Hr_Inund_Phase_C) %>%
  na.omit() -> only.inund.3

cormat <- cor(only.inund.3)

melted.cormat <- reshape2::melt(cormat)

ggplot(data = melted.cormat ) + 
  geom_tile(aes(x=Var1, y=Var2, fill=value)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 9, hjust = 1))


```

Can we predict hatching success using these predictors?

```{r}
response <- only.inund.2$p_success

predictors <- only.inund.2 %>% select(-c(p_success, f_Season, Season))
RF.data <- as.data.frame(scale(predictors))

RF.data$p_success <- response
RF.data$RV <- runif(nrow(RF.data), 0, 1)
```



```{r}

ntree <- 500

M.3 <- as.formula("p_success ~ Nest_Elevation + 
                  Berm_Dist + 
                  Max_Height + 
                  n_Inundation + 
                  Max_Inund_Duration_Hr +
                  Total_Inund_Duration_Hr + 
                  Mean_Inund_Duration_Hr +
                  Prop_Inund_Duration + 
                  SD_Inund_Duration_Hr +
                  Mean_Max_Height_Per_Event +
                  SD_Max_Height_Per_Event +
                  n_Inund_Phase_A +
                  n_Inund_Phase_B +
                  n_Inund_Phase_C +
                  Hr_Inund_Phase_A +
                  Hr_Inund_Phase_B +
                  Hr_Inund_Phase_C +
                  RV")

RF.M.3 <- cforest(formula = M.3,
                  data = RF.data,
                  control = cforest_unbiased(ntree = ntree,
                                             trace = 500))
saveRDS(RF.M.3, file = "RData/RF_M_3_out.rds")

var.imp <- sort(varimp(RF.M.3), decreasing = FALSE)
saveRDS(var.imp, file = "RData/RF_M_3_varImp.rds")

pred.RF.M.3 <- RF.M.3@predict_response()

```


Look at the variable importance:
```{r}
var.imp.df <- data.frame(var.imp)
var.imp.df$Variable <- rownames(var.imp.df)

ggplot(data = var.imp.df) + 
  geom_point(aes(x = var.imp, y = reorder(Variable, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))
```

They seem to affect hatching success somewhat. Interesting to find that Phase B (18-36 days of incubation) affects more than other phases. 

```{r}
RF.data$p.success.prediction <- pred.RF.M.3
ggplot(data = RF.data) +
  geom_point(aes(x = p_success, y = p.success.prediction)) + 
  geom_abline(slope = 1.0, intercept = 0.0) + 
  ylim(c(0, 1)) + 
  labs(x = "Observed success rate", 
       y = "Predicted success rate")

```

Can't predict... This is disappointing... 

Try beta regression (betareg)

```{r}
library(betareg)
betareg.data <- RF.data
betareg.data$p.success.2 <- RF.data$p_success
betareg.data$p.success.2[betareg.data$p_success > 0.999] <- 0.999
betareg.data$p.success.2[betareg.data$p_success < 0.001] <- 0.001
betareg.data$f_Season <- only.inund.2$f_Season

fit.betareg.1 <- betareg(p.success.2 ~ Berm_Dist + Max_Height + Mean_Max_Height_Per_Event + Hr_Inund_Phase_B + n_Inund_Phase_B + f_Season,
                         data = betareg.data)

summary(fit.betareg.1)
```

Hours and the number of inundation during phase B (18-36 days of incubation; middle third) seem to affect the proportion of hatching success, although the signs are opposite. 

Including more predictors doesn't help tune the model.

```{r}
fit.betareg.2 <- betareg(p.success.2 ~ Berm_Dist + Max_Height + Mean_Max_Height_Per_Event + Hr_Inund_Phase_B + n_Inund_Phase_B ,
                         data = betareg.data)

summary(fit.betareg.2)
```



```{r}
fit.betareg.3 <- betareg(p.success.2 ~ Berm_Dist + Max_Height + Mean_Max_Height_Per_Event + Hr_Inund_Phase_B ,
                         data = betareg.data)

summary(fit.betareg.3)
```


Let's try doing this in the Bayesian regression.


```{r}
response <- only.inund.2$p_success
# get rid of non-numeric variables
predictors <- only.inund.2 %>% select(-c(p_success, f_Season, Season))
Bayes.data <- as.data.frame(scale(predictors))
Bayes.data$Season <- ifelse(only.inund.2$f_Season == "17/18", 0, 1)

library(jagsUI)
library(bayesplot)

jags.data <- list(y = response,
                  X1 = Bayes.data$Max_Height,
                  X2 = Bayes.data$Mean_Max_Height_Per_Event,
                  X3 = Bayes.data$Hr_Inund_Phase_B,
                  X4 = Bayes.data$n_Inund_Phase_B,
                  X5 = Bayes.data$Berm_Dist,
                  X6 = Bayes.data$Season,
                  N = nrow(Bayes.data))

MCMC.params <- list(n.samples = 10000,
                    n.burnin = 5000,
                    n.thin = 5,
                    n.chains = 5)

MCMC.params$model.file = "models/Model_logit_hatching.txt"

parameters <- c("b0", "b1", "b2", "b3", "b4", "b5", "b6",
                "sigma.y", "loglik", "deviance")

jm.2 <- jags(data = jags.data,
             #inits = inits,
             parameters.to.save= parameters,
             model.file = MCMC.params$model.file,
             n.chains = MCMC.params$n.chains,
             n.burnin = MCMC.params$n.burnin,
             n.thin = MCMC.params$n.thin,
             n.iter = MCMC.params$n.samples,
             DIC = T, 
             parallel=T)

```



 