---
title: "R Notebook"
output: html_notebook
---

In this Notebook, I use the second-order polynomial function fitted to the inundation data in Inundation_v2.Rmd to evaluate probabilities of inundation for nests. This version (v.2) computes new measures:

1. Compute proportions of phase-1 deaths (Yes, and to adjust proportion (%) of phase 1 deaths from % of failed eggs to % of total eggs recovered for each nest) for all nests. Then look at how they are affected by the inundation line for the first 30 days of incubation. I'm envisioning this to be plots similar to the last ones but change the hatch success to proportion of phase-1 deaths.

2.   For each nest, compute the height above inundation line (+/- 95% confidence intervals). 

Yep, that’d be great and yes, for max inundation heights for each of the 3 months post laying. These curves look good.

For this version (v.4), I try to fulfill the following request from Owen Coffee (2020-08-04):

"The updated inundation logger .csv now contains the inundation heights for all highs in a month above the median (each max in the tidal cycle + ~ 2 days either side) not just the max as was previously used. As you have said, bottom/mid/complete can be calculated from each individual nest depth so really the difference in the analysis is now not just determining inundation from the max monthly high for each incubation month, but how many of the identified highs above median for each month (1st, 2nd and 3rd month of incubation) would correspond with each of bottom/mid/complete inundation for the considered nests. The hope would then be to estimate the total period immersed for each of those inundation events from what Andy is working on, and then whether the timing (early/mid/late development), frequency or period of inundation correlates with clutch mortality."

It turned out that he wanted me to fit multiple lines within each month - done in inundation_v4.Rmd. Results are brought in here. 

Load essential libraries.

```{r}
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(readr)
library(lubridate)
library(jagsUI)
library(bayesplot)
library(party)
#library(rfPermute)
#library(randomForestExplainer)
source("Dunstan_Inundation_fcns.R")
```

And load the data.

```{r}
#Transect,Post,Date,Time,Aspect,Survey Date,Inundation Month,Dist_from_Berm,Beach_Elevation,Inund_Height
inund.cols <- cols(
   Transect = col_double(),
   Post = col_double(),
   Date = col_date(format = "%d/%m/%Y"),
   Time = col_time(format = "%H:%M:%S %p"),
   Aspect = col_character(),
   Survey_Date = col_character(),
   Inundation_Month = col_character(),
   Dist_from_Berm = col_double(),
   Beach_Elevation = col_double(),
   Inund_Height = col_double())

inund <- read_csv("data/inundationRaine_abovemedian.csv", col_types = inund.cols)
inund %>% filter(Transect != 2) %>%
  mutate(Transect_f = as.factor(Transect),
         Year = ifelse(Date < as.Date("2018-05-01"), 2018, 2019),
         Year2 = ifelse(Year == 2018, 1, 2),
         Transect2 = Transect - 1,
         log_inund = log(Inund_Height)) %>% 
  arrange(Date) %>% 
  filter((Date < as.Date("2017-12-08") | Date > as.Date("2017-12-14"))) %>%  # remove between 12-08 and 12-04 
  filter(Date != as.Date("2017-12-31")) -> inund

# define datasets by looking at difference in consecutive dates.
dt <- as.numeric(inund$Date[2:length(inund$Date)] - inund$Date[1:(length(inund$Date)-1)])
inund$dt <- c(0, dt)
inund$dataset.ID <- cumsum(ifelse(inund$dt < 2, 0, 1)) + 1

# Datasets are defined by how data are combined among close dates. So, sometimes, they go over two
# months. These have to be assigned to the same month as the first data point of the particular
# dataset.
inund %>% group_by(dataset.ID) %>%
  mutate(Month = month(nth(Date, 3)),
         Month2 = ifelse(Month > 9, Month - 9, Month + 3),
         Month_f = factor(Month, levels = c("10", "11", "12", "1", "2", "3", "4"))) -> inund


# for each month, I want to find out which datasets represent the highest and lowest tides, assign values for later use. Sometimes there is only one dataset per month and as many as four. 
y <- m <- 1
tide.order <- data.frame(tide.order = NA,
                         dataset.ID = NA) 

m <- 7
for (y in 1:2){
  for (m in 1:7){
    inund %>% filter(Year2 == y & Month2 == m) %>%
      select(dataset.ID) %>% 
      unique() -> unique.ID
    
      inund %>% filter(dataset.ID %in% unlist(unique.ID)) %>%
        group_by(dataset.ID) %>%
        summarise(tide.height = first(Inund_Height)) %>%
        arrange(by = desc(tide.height)) %>%
        rownames_to_column("tide.order" ) %>% #-> tmp #
        select(tide.order, dataset.ID)  %>%
        rbind(tide.order) -> tide.order
        
  }
}

tide.order %>% 
  na.omit() %>% 
  right_join(inund, by = "dataset.ID") -> inund

min.Dist <- min(inund$log_inund)
sd.Dist <- sqrt(var(inund$log_inund))

# create dataset vs. month/year look up table
inund %>% 
  select(dataset.ID, Month, Month2, Year2, Date) %>% 
  group_by(dataset.ID) %>% 
  summarise(Month = first(Month), 
            Month2 = first(Month2),
            Year2 = first(Year2),
            first.date = first(Date)) %>%
  left_join(na.omit(tide.order))-> dataset_def 

nest.cols <- cols(fid = col_integer(), 
                  Nest_UID = col_character(), 
                  Northings = col_double(), 
                  Eastings = col_double(), 
                  Aspect = col_character(),
                  Nest_Elevation = col_double(),
                  Berm_Dist = col_double(),
                  Date_laid = col_date(format = "%d/%m/%Y"),
                  Date_dug = col_date(format = "%d/%m/%Y"),
                  Sector = col_character(),
                  Habitat = col_character(),
                  Hatched = col_integer(),
                  Live_hatchlings = col_integer(),
                  Dead_hatchlings = col_integer(),
                  Phase_1 = col_integer(),
                  Phase_2 = col_integer(),
                  Phase_3 = col_integer(),
                  Phase_4 = col_integer(),
                  Phase_5 = col_integer(),
                  Phase_6 = col_integer(),
                  Decomposed = col_integer(),
                  Total_unhatched = col_integer(),
                  Total_clutch = col_integer(),
                  rate_success = col_double(),
                  Season_Peakpop = col_integer())

# the following file was created from revised data from Owen Coffee (nest_inund_prediction_OCedits.csv).
nest.data <- read_csv("data/hatchsuccess_inund.csv", 
                      col_types = nest.cols)

nest.data %>% 
  mutate(Year = ifelse(Date_laid < as.Date("2018-05-01"), 2018, 2019),
         Month = month(Date_laid),
         Month2 = ifelse(Month > 9, Month - 9, Month + 3),
         Month_f = factor(Month, levels = c("10", "11", "12", "1", "2", "3", "4")),
         scaled_Dist_Berm = (log(Berm_Dist) - min.Dist)/sd.Dist,
         Phase_1_death = Phase_1/Total_clutch,
         Phase_2_death = Phase_2/Total_clutch) -> nest.data

```


Second order polynomial with month-specific intercept and coefficients for the distance plus year effect:

mu.y[i] <- b0[month[i], year[i]] + b1[month[i]] * Dist_Berm[i] + b12[month[i]] * Dist_Berm[i] * Dist_Berm[i]

y[i] ~ dnorm(mu.y[i], tau.y)  

Results of model fitting is saved in a .rds file (ran in inundation_Nests_v2.Rmd).
```{r}
jm.2 <- readRDS("RData/Poly2_dataset_month_year_aboveMed.rds")

jags.data <- jm.2$model$cluster1$data()
# jags.data <- list(dataset.ID = inund$dataset.ID,
#                   y = inund$log_inund,
#                   month = inund$Month2,
#                   Dist_Berm = inund$Dist_from_Berm,
#                   year = inund$Year2,
#                   N = nrow(inund),
#                   n.dataset = length(unique(inund$dataset.ID)),
#                   n.years = length(unique(inund$Year2)),
#                   n.months = length(unique(inund$Month2)))

MCMC.params <- list(n.samples = jm.2$mcmc.info$n.samples,
                    n.burnin = jm.2$mcmc.info$n.burnin,
                    n.thin = jm.2$mcmc.info$n.thin,
                    n.chains = jm.2$mcmc.info$n.chains)

#model.file = "models/Model_Poly2_month_year.txt")

parameters <- c("b0", "b1", "b2", "b12", "sigma.y",
                 "fit", "fit.new", "deviance")


```


Extract the posterior samples and create plots
```{r}
pred.list.jm.2.1 <- extract.prediction.poly2.dataset.month(zm = jm.2, 
                                                           jags.data = jags.data, 
                                                           dataset_def = dataset_def)

sigma.y <- quantile(pred.list.jm.2.1$sigma.y, 0.5)

# need to transform dataset ID to month:
pred.list.jm.2.1$pred.df %>% left_join(dataset_def, by = "dataset.ID") -> pred.df.jm.2.1

pred.df.jm.2.1 %>% 
  mutate(Year = Year2 + 2017,
         Month_f = factor(Month, 
                          levels = c("10", "11", "12", "1", "2", "3", "4"))) -> pred.df.jm.2.1


p.1 <- ggplot() + 
  geom_point(data = inund,
             aes(x = (Dist_from_Berm),
                 y = log(Inund_Height))) +
  geom_path(data = pred.df.jm.2.1,
            aes(x = Dist_Berm,
                y = (pred_med),
                group = dataset.ID)) +
  geom_ribbon(data = pred.df.jm.2.1,
              aes(x = Dist_Berm,
                  ymin = (pred_low),
                  ymax = (pred_high),
                  group = dataset.ID),
              alpha = 0.5) +
  geom_ribbon(data = pred.df.jm.2.1,
              aes(ymin = pred_med - median(sigma.y) * 2,
                  ymax = pred_med + median(sigma.y) * 2,
                  x = Dist_Berm,
                  group = dataset.ID,
                  fill = tide.order),
              alpha = 0.4) +
  facet_grid(Year ~ Month_f)  +
     geom_point(data = nest.data,
              aes(x = Berm_Dist,
                  y = log(Nest_Elevation),
                  color = rate_success),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Predicted inundation height and success rate")

#theme(legend.position = "none") 
# ggsave(plot = p.1, filename = "figures/inundation_success_aboveMedian.png",
#        device = "png", dpi = 600)

p.1
```

We somewhat agreed on the following steps using these regression lines.

1. Take a nest and determine the nest elevation (e.g., 3.72 for 1712-001) - The nest elevations are all measured from the bottom of the nest.
2. Determine bottom/middle/complete inundation heights for the j-th nest , which are computed from the nest elevation and its definition. Let's call them H_bottom_j, H_middle_j, and H_complete_j.
3. Count how many of recorded above-median tide heights during the X days (please specify how many days) of incubation (provided in inundationRaine_abovemedian.csv) were greater than H_bottom_j, H_middle_j, and H_complete_j. 

OC: Yes, this is how I see it, my only question to point 3 would be that while we now have a better spread of heights across the month that may correspond with inundation events for the nests, do we not still need to develop a curve for each event to estimate the height of inundation along the beach profile for those nests not located in proximity to an inundation logger?

OC: Katharine and I have looked back through the most recent incubation period results we have which include work done on Milman island and on Raine island in the last two nesting seasons. Both of these are suggesting an incubation period of approximately 50-52 days. For Raine island, the nests considered in this study for the 18-19 season had mean incubation periods of 49.1 days for October (range 47.5 - 55.5) and December  (range 48.1 - 51.1) and 51.7 days for nests laid in Feb (range 49.7 - 54.4). I think based on these results we could say with reasonable confidence that an incubation period of 50 days from the date laid in the nest file will encompass the majority of nests considered.

So... we need to look at the date each nest was laid and dates of high tides. Also the duration of incubation should be changed to 50 days rather than 3 months that were used previously. 

```{r}
# find predicted inundation height at each observed nest
nest.data %>% select(Nest_UID, Date_laid, Month2, Year, Berm_Dist) %>%
  mutate(Year = ifelse(Year == 2018, 1, 2),
         Date_end = Date_laid + 50,
         Date_middle = Date_laid + 25,
         Month_begin = month(Date_laid),
         Month_end = month(Date_end),
         Month_middle = month(Date_middle),
         Month2_begin = ifelse(Month_begin > 9, Month_begin - 9, Month_begin + 3),
         Month2_end = ifelse(Month_end > 9, Month_end - 9, Month_end + 3),
         Month2_middle = ifelse(Month_end > 9, Month_end - 9, Month_end + 3)) -> new.data

# predict for the first month - this may be disregarded if high tide was recorded
# prior to nest deposition
new.data.begin <- new.data %>% transmute(Year = Year,
                                         Berm_Dist = Berm_Dist,
                                         Month = Month2_begin,
                                         Date_begin = Date_laid,
                                         Date_end = Date_end)

pred.data.month.begin <- predict.poly2.dataset.month(zm = jm.2, 
                                                     new.data = new.data.begin, 
                                                     dataset_def = dataset_def)

new.data.middle <- new.data %>% transmute(Year = Year,
                                          Berm_Dist = Berm_Dist,
                                          Month = Month2_middle,
                                          Date_begin = Date_laid,
                                          Date_end = Date_end)

pred.data.month.middle <- predict.poly2.dataset.month(zm = jm.2, 
                                                      new.data = new.data.middle, 
                                                      dataset_def = dataset_def)

# new.data.end <- new.data %>% transmute(Year = Year,
#                                        Berm_Dist = Berm_Dist,
#                                        Month = Month2_end,
#                                        Date_begin = Date_laid,
#                                        Date_end = Date_end) 
# 
# pred.data.month.end <- predict.poly2.dataset.month(zm = jm.2, 
#                                                    new.data = new.data.end, 
#                                                    dataset_def = dataset_def)

# determine whether each inundation event should be included based on when the nest was
# laid and when the high tide occurred. 
# This part was done in the function. 

# figure out the approximate 95% intervals for data uncertainty at each nest 
# and determine if the nest height was above the upper bound
# look at bottom of the nest (Nest_Elevation + 0.01), half way up (Nest_Elevation + 0.3),
# and all the way (Nest_Elevation + 0.6) (I made up 0.6 m so need a correct number.)
nest.full <- 0.3
nest.half <- 0.15

n.inund.half <- data.frame(Nest_UID = NA, n.half.Month.1 = NA, n.half.Month.2 = NA)
n.inund.full  <- data.frame(Nest_UID = NA, n.full.Month.1 = NA, n.full.Month.2 = NA)

k <- 1
for(k in 1:nrow(new.data)){
  n.inund.full[k, "Nest_UID"] <- new.data$Nest_UID[k]
  n.inund.half[k, "Nest_UID"] <- new.data$Nest_UID[k]
  
  # find which ones should be included - TRUE/FALSE
  tides.in.begin <- pred.data.month.begin$data.idx[[k]]$tide.in
  median.heights.begin <- as.numeric(list2DF(pred.data.month.begin$qtiles[[k]])[2, tides.in.begin])
  upper.heights.begin <- median.heights.begin + (1.96 * median(sigma.y))  # sigma.y is from log scale
  nest.height <- as.numeric(log(nest.data[k, "Nest_Elevation"]))  # in log scale
  
  n.inund.half[k, "n.half.Month.1"] <- sum(upper.heights.begin > log(exp(nest.height) + nest.half), na.rm = T)
  n.inund.full[k, "n.full.Month.1"] <- sum(upper.heights.begin > log(exp(nest.height) + nest.full), na.rm = T )

  # find which ones should be included - TRUE/FALSE
  # This can be the same as the begin month...
  if (new.data.begin[k, "Month"] != new.data.middle[k, "Month"]){  
    tides.in.middle <- pred.data.month.middle$data.idx[[k]]$tide.in
    median.heights.middle <- as.numeric(list2DF(pred.data.month.middle$qtiles[[k]])[2, tides.in.middle])
    upper.heights.middle <- median.heights.middle + (1.96 * median(sigma.y))
    n.inund.half[k, "n.half.Month.2"] <- sum(upper.heights.middle > log(exp(nest.height) + nest.half), na.rm = T )
    n.inund.full[k, "n.full.Month.2"] <- sum(upper.heights.middle > log(exp(nest.height) + nest.full), na.rm = T )
  }  
  
  # # find which ones should be included - TRUE/FALSE 
  # # this can be the same as the middle month, so check that first
  # if (new.data.middle[k, "Month"] != new.data.end[k, "Month"]){  
  #   tides.in.end <- pred.data.month.end$data.idx[[k]]$tide.in
  #   median.heights.end <- as.numeric(list2DF(pred.data.month.end$qtiles[[k]])[2, tides.in.end])
  #   upper.heights.end <- median.heights.end + (1.96 * median(sigma.y))
  #   n.inund.half[k, "Month.end"] <- sum(upper.heights.end > log(exp(nest.height) + nest.half), na.rm = T)
  #   n.inund.full[k, "Month.end"] <- sum(upper.heights.end > log(exp(nest.height) + nest.full), na.rm = T )
  # }

}

# turns out Month.end were all NAs

nest.data %>% select(fid, Nest_UID, Date_laid, Northings, Eastings, 
                     Nest_Elevation, Berm_Dist, Total_clutch, 
                     Habitat, rate_success, Year, Month2, 
                     Habitat, Phase_1_death, Month_f) %>%
  mutate(Date_end = Date_laid + 50) %>%
  left_join(n.inund.full, by = "Nest_UID") %>%
  left_join(n.inund.half, by = "Nest_UID") -> nest.data.2

write_csv(nest.data.2, path = "data/nest_data_inundation.csv")

#nest.data.2 %>% na.omit() -> nest.data.2
set.seed(12345)

nest.data.2$RV <- runif(n = nrow(nest.data.2), min = 0, max = 1)
```


```{r}
p.2_1 <- ggplot() + 
  geom_point(data = inund,
             aes(x = (Dist_from_Berm),
                 y = log(Inund_Height))) +
  geom_path(data = pred.df.jm.2.1,
            aes(x = Dist_Berm,
                y = (pred_med),
                group = dataset.ID)) +
  geom_ribbon(data = pred.df.jm.2.1,
              aes(x = Dist_Berm,
                  ymin = (pred_low),
                  ymax = (pred_high),
                  group = dataset.ID),
              alpha = 0.5) +
  geom_ribbon(data = pred.df.jm.2.1,
              aes(ymin = pred_med - median(sigma.y) * 2,
                  ymax = pred_med + median(sigma.y) * 2,
                  x = Dist_Berm,
                  group = dataset.ID,
                  fill = tide.order),
              alpha = 0.4) +
#  facet_grid(Year ~ Month_f)  +
     geom_point(data = nest.data.2,
              aes(x = Berm_Dist,
                  y = log(Nest_Elevation + nest.full),
                  color = as.factor(n.full.Month.1)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Predicted tide height and # inundation during first month") + 
  guides(fill = FALSE) + 
  scale_color_discrete(name = "# inund")

p.2_1
```


```{r}
p.2_2 <- ggplot() + 
  geom_point(data = inund,
             aes(x = (Dist_from_Berm),
                 y = log(Inund_Height))) +
  geom_path(data = pred.df.jm.2.1,
            aes(x = Dist_Berm,
                y = (pred_med),
                group = dataset.ID)) +
  geom_ribbon(data = pred.df.jm.2.1,
              aes(x = Dist_Berm,
                  ymin = (pred_low),
                  ymax = (pred_high),
                  group = dataset.ID),
              alpha = 0.5) +
  geom_ribbon(data = pred.df.jm.2.1,
              aes(ymin = pred_med - median(sigma.y) * 2,
                  ymax = pred_med + median(sigma.y) * 2,
                  x = Dist_Berm,
                  group = dataset.ID,
                  fill = tide.order),
              alpha = 0.4) +
#  facet_grid(Year ~ Month_f)  +
     geom_point(data = nest.data.2,
              aes(x = Berm_Dist,
                  y = log(Nest_Elevation + nest.full),
                  color = as.factor(n.full.Month.2)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Predicted tide height and # inundation during second month") + 
  guides(fill = FALSE) + 
  scale_color_discrete(name = "# inund")

p.2_2
```



Can we predict Phase_1_death with all possible variables using random forest?

```{r}
ntree <- 500

M.1 <- as.formula("rate_success ~ Berm_Dist + 
                    Total_clutch +
                  Year +
                  Nest_Elevation + 
                  Northings +
                  Eastings +
                  n.half.Month.1 + 
                  n.half.Month.2 + 
                  n.full.Month.1 + 
                  n.full.Month.2 +
                  RV")

if (!file.exists("RData/RF_M_1_out.rds")){
  RF.M.1 <- cforest(formula = M.1,
                    data = nest.data.2,
                    control = cforest_unbiased(ntree = ntree,
                                               trace = 500))
  saveRDS(RF.M.1, file = "RData/RF_M_1_out.rds")
} else {
  RF.M.1 <- readRDS("RData/RF_M_1_out.rds")
}

if (!file.exists("RData/RF_M_1_varImp.rds")){
  var.imp <- sort(varimp(RF.M.1), decreasing = FALSE)
  saveRDS(var.imp, file = "RData/RF_M_1_varImp.rds")
} else {
  var.imp <- readRDS("RData/RF_M_1_varImp.rds")
}

if (!file.exists("RData/RF_M_1_predict.rds")){
  pred.RF.M.1 <- predict(RF.M.1, newdata = NULL)
  saveRDS(pred.RF.M.1, file = "RData/RF_M_1_predict.rds")
} else {
  pred.RF.M.1 <- readRDS("RData/RF_M_1_predict.rds")
}

```


Look at the variable importance:
```{r}
var.imp.df <- data.frame(var.imp)
var.imp.df$Variable <- rownames(var.imp.df)

ggplot(data = var.imp.df) + 
  geom_point(aes(x = var.imp, y = reorder(Variable, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))
```




Compare the data and predictions:

```{r}
nest.data.2$rate_success_prediction <- pred.RF.M.1[,1]
ggplot(data = nest.data.2) +
  geom_point(aes(x = rate_success, y = rate_success_prediction)) + 
  geom_abline(slope = 1.0, intercept = 0.0) + 
  #ylim(c(0, 1)) + 
  labs(x = "Observed success rate", 
       y = "Predicted success rate")

```


```{r}
fit.1 <- lm(rate_success_prediction ~ rate_success, data = nest.data.2)
summary(fit.1)
```

How about Phase 1 deaths?


```{r}
M.2 <- as.formula("Phase_1_death ~ Berm_Dist + 
                    Total_clutch +
                  Year +
                  Nest_Elevation + 
                  Northings +
                  Eastings +
                  n.half.Month.1 + 
                  n.half.Month.2 + 
                  n.full.Month.1 + 
                  n.full.Month.2 +
                  RV")

if (!file.exists("RData/RF_M_2_out.rds")){
  RF.M.2 <- cforest(formula = M.2,
                    data = nest.data.2,
                    control = cforest_unbiased(ntree = ntree,
                                               trace = 500))
  saveRDS(RF.M.2, file = "RData/RF_M_2_out.rds")
} else {
  RF.M.2 <- readRDS("RData/RF_M_2_out.rds")
}

if (!file.exists("RData/RF_M_2_varImp.rds")){
  var.imp <- sort(varimp(RF.M.2), decreasing = FALSE)
  saveRDS(var.imp, file = "RData/RF_M_2_varImp.rds")
} else {
  var.imp <- readRDS("RData/RF_M_2_varImp.rds")
}

if (!file.exists("RData/RF_M_2_predict.rds")){
  pred.RF.M.2 <- predict(RF.M.2, newdata = NULL)
  saveRDS(pred.RF.M.2, file = "RData/RF_M_2_predict.rds")
} else {
  pred.RF.M.2 <- readRDS("RData/RF_M_2_predict.rds")
}
```

Look at the variable importance:
```{r}
var.imp.df <- data.frame(var.imp)
var.imp.df$Variable <- rownames(var.imp.df)

ggplot(data = var.imp.df) + 
  geom_point(aes(x = var.imp, y = reorder(Variable, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))
```

Compare the data and predictions:

```{r}
nest.data.2$Phase_1_death_prediction <- pred.RF.M.2[,1]
ggplot(data = nest.data.2) +
  geom_point(aes(x = Phase_1_death, y = Phase_1_death_prediction)) + 
  geom_abline(slope = 1.0, intercept = 0.0) + 
  #ylim(c(0, 1)) + 
  labs(x = "Observed success rate", 
       y = "Predicted success rate")

```


```{r}
fit.2 <- lm(Phase_1_death_prediction ~ Phase_1_death, data = nest.data.2)
summary(fit.2)
```
