---
title: "R Notebook"
output: html_notebook
---

Examining relationships between inundation height and various environmental variables. 

```{r}
rm(list = ls())

library("tidyverse")
library("lubridate")

```

Bring in the data files

```{r}
inund_cols <- cols(Transect = col_integer(),
                   Post = col_integer(),
                   InundHeight_AbvLAT = col_double(),
                   Dist_Berm = col_double(),
                   Berm_elevation = col_double(),
                   BermSurvey_Month = col_character(),
                   Inund_Month = col_character(),
                   Date = col_date(format = "%d/%m/%Y"),
                   Time = col_time(format = ""))

inund <- read_csv("data/inundationRaine.csv", col_types = inund_cols) 

Nest_cols <- cols(Nest_ID = col_integer(),
                  Nest_Easting = col_double(),
                  Nest_Northing = col_double(),
                  Nest_Elevation = col_double(),
                  BermDist_m = col_double(),
                  inundated = col_character())

Nest_18INUND <- read_csv("data/2018Nest_INUND.csv",
                         col_types = Nest_cols)  

Agg_cols <- cols(Date = col_date(format = "%d/%m/%Y"),
                 T2_4 = col_double(),
                 T3_1 = col_double(),
                 T3_2 = col_double(),
                 T4_1 = col_double(),
                 T4_2 = col_double(),
                 T4_3 = col_double(),
                 T4_4 = col_double(),
                 T5_1 = col_double(),
                 T5_2 = col_double(),
                 T5_4 = col_double(),
                 'Barometric Pressure (Hpa)' = col_double(),
                 'Rainfall (mm)' = col_double(),
                 'Tide Height' = col_double(),
                 MAX_Wind = col_double(),
                 MAX_AVGWind = col_double())

Agg_INUND <- read_csv("data/Inund_concat.csv",
                      col_types = Agg_cols) %>%
  rename(T_Height = 'Tide Height',
         Rainfall = 'Rainfall (mm)',
         Baro_Press = 'Barometric Pressure (Hpa)')

# Regular expression "." is a wildcard, so T._. includes all column names with T in the first position and _ in the third position, whereas 2nd and 4th position can be anything. 
Agg_INUND %>% select(Date, matches("T._.")) -> Agg_INUND_loggers

Agg_INUND_loggers %>% 
  pivot_longer(!Date, names_to = "logger", values_to = "height") -> Agg_INUND_loggers_long

# get just environmental variables
Agg_INUND %>% select(Date, !matches("T._.")) -> Agg_INUND_enviro

Agg_INUND %>% select(Date, c(T_Height, matches("T._."))) -> Agg_INUND_T_Height
Agg_INUND_T_Height %>% 
  pivot_longer(!c(Date, T_Height), names_to = "logger", values_to = "height") -> Agg_INUND_T_Height_long

Agg_INUND %>% select(Date, c(Rainfall, matches("T._."))) -> Agg_INUND_Rainfall
Agg_INUND_Rainfall %>%
  pivot_longer(!c(Date, Rainfall), names_to = "logger", values_to = "height") -> Agg_INUND_Rainfall_long

Agg_INUND %>% select(Date, c(Baro_Press, matches("T._."))) -> Agg_INUND_Baro
Agg_INUND_Baro %>%
  pivot_longer(!c(Date, Baro_Press), names_to = "logger", values_to = "height") -> Agg_INUND_Baro_long

Agg_INUND %>% select(Date, c(MAX_Wind, matches("T._."))) -> Agg_INUND_MAX_Wind
Agg_INUND_MAX_Wind %>%
  pivot_longer(!c(Date, MAX_Wind), names_to = "logger", values_to = "height") -> Agg_INUND_MAX_Wind_long

Agg_INUND %>% select(Date, c(MAX_AVGWind, matches("T._."))) -> Agg_INUND_MAX_AVGWind
Agg_INUND_MAX_AVGWind %>%
  pivot_longer(!c(Date, MAX_AVGWind), names_to = "logger", values_to = "height") -> Agg_INUND_MAX_AVGWind_long

# 
# #Wells_5Apr16 <- read_csv("CSVs/DirectWells_5April2016.csv")
# Wells_5Apr16 <- read_csv("data/DirectWells_5April2016.csv")  # TE
#  Wells_5Apr16 <- Wells_5Apr16[c(-9)]
#   Wells_5Apr16 <- na.omit(Wells_5Apr16) 
#    
# # Wells_6Apr16 <- read_csv("CSVs/DirectWells_6April2016.csv")
# #  
# # Tides_Apr16 <- read_csv("CSVs/PredictedTides_April2016.csv")
# #  
# # inund_Apr16 <- read_csv("CSVs/InundLoggers_April2016.csv")
#  
# Wells_6Apr16 <- read_csv("data/DirectWells_6April2016.csv")  # TE
#  
# Tides_Apr16 <- read_csv("data/PredictedTides_April2016.csv")  # TE
#  
# inund_Apr16 <- read_csv("data/InundLoggers_April2016.csv")  # TE
 
 
```


Density plot of height
```{r}

ggplot(Agg_INUND_loggers_long) +
  geom_density(aes(x = height)) + 
  facet_wrap(~ as.factor(logger))

```

Some are more "normal" than others... 


Scatter plots between loggers and environmental variables 

```{r}
ggplot(Agg_INUND_T_Height_long) +
  geom_point(aes(x = T_Height, y = height)) + 
  facet_wrap(~ as.factor(logger))


```

Some are "more" linear than others. 



```{r}
ggplot(Agg_INUND_Rainfall_long) +
  geom_point(aes(x = Rainfall, y = height)) + 
  facet_wrap(~ as.factor(logger))


```

There aren't much of relationships in these plots. 

```{r}
ggplot(Agg_INUND_Baro_long) +
  geom_point(aes(x = Baro_Press, y = height)) + 
  facet_wrap(~ as.factor(logger))


```

Not much relationships here either. 



```{r}
ggplot(Agg_INUND_MAX_Wind_long) +
  geom_point(aes(x = MAX_Wind, y = height)) + 
  facet_wrap(~ as.factor(logger))


```

No relationship... 


```{r}
ggplot(Agg_INUND_MAX_AVGWind_long) +
  geom_point(aes(x = MAX_AVGWind, y = height)) + 
  facet_wrap(~ as.factor(logger))


```

Not here either... 

Time series plots:

```{r}
ggplot(data = Agg_INUND_loggers_long) + 
  geom_path(aes(x = Date, y = height, color = as.factor(logger)))
```


