---
title: "R Notebook"
output: html_notebook
---

In this Notebook, I use the second-order polynomial function fitted to the inundation data in Inundation_v2.Rmd to evaluate probabilities of inundation for nests. 


Load essential libraries first.

```{r}
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(readr)
library(lubridate)
library(jagsUI)
library(bayesplot)

source("Dunstan_Inundation_fcns.R")
```

And load the data.

```{r}

inund.cols <- cols(
   Transect = col_double(),
   Post = col_double(),
   InundHeight_AbvLAT = col_double(),
   Dist_Berm = col_double(),
   Berm_elevation = col_double(),
   BermSurvey_Month = col_character(),
   Inund_Month = col_character(),
   Date = col_date(format = "%d/%m/%Y"),
   Time = col_time(format = "%H:%M:%S %p"))

inund <- read_csv("data/inundationRaine.csv", col_types = inund.cols)
min.Dist <- min(inund$Dist_Berm)
sd.Dist <- sqrt(var(inund$Dist_Berm))

inund %>% mutate(Year = ifelse(Date < as.Date("2018-05-01"), 2018, 2019)) %>%
  mutate(Month = month(Date)) %>%
  filter(Transect != 2) %>%
  mutate(Transect_f = as.factor(Transect),
         Year2 = ifelse(Year == 2018, 1, 2),
         Month2 = ifelse(Month > 9, Month - 9, Month + 3),
         Month_f = factor(Month, levels = c("10", "11", "12", "1", "2", "3", "4")),
         Transect2 = Transect - 1,
         log_inund = log(InundHeight_AbvLAT),
         scaled_Dist_Berm = (Dist_Berm - min.Dist)/sd.Dist) -> inund

inund.2018 <- filter(inund, Year == 2018)
inund.2019 <- filter(inund, Year == 2019)

#View(inund)
# Replaced Feb-18 with 15/02/2018 (TE, 2020-03-19)
# Replaced Dec-18 with 15/12/2018 (TE, 2020-03-19)
# Replaced Feb-20 with 15/02/2020 (TE, 2020-03-19)

nest.cols <- cols(fid = col_integer(), 
                  Nest_UID = col_character(), 
                  Northings = col_double(), 
                  Eastings = col_double(), 
                  Nest_Elevation = col_double(),
                  Berm_Dist = col_double(),
                  Date_laid = col_date(format = "%d/%m/%Y"),
                  Date_dug = col_date(format = "%d/%m/%Y"),
                  Sector = col_character(),
                  Habitat = col_character(),
                  Hatched = col_integer(),
                  Live_hatchlings = col_integer(),
                  Dead_hatchlings = col_integer(),
                  Phase_1 = col_integer(),
                  Phase_2 = col_integer(),
                  Phase_3 = col_integer(),
                  Phase_4 = col_integer(),
                  Phase_5 = col_integer(),
                  Phase_6 = col_integer(),
                  Decomposed = col_integer(),
                  Total_unhatched = col_integer(),
                  Total_clutch = col_integer(),
                  rate_success = col_double())

nest.data <- read_csv("data/hatchsuccess_inund_TE.csv", 
                      col_types = nest.cols)

nest.data %>% mutate(Year = ifelse(Date_laid < as.Date("2018-05-01"), 2018, 2019)) %>%
  mutate(Month = month(Date_laid),
         Month2 = ifelse(Month > 9, Month - 9, Month + 3),
         Month_f = factor(Month, levels = c("10", "11", "12", "1", "2", "3", "4")),
         scaled_Dist_Berm = (Berm_Dist - min.Dist)/sd.Dist) -> nest.data

```


Second order polynomial with month-specific intercept and coefficients for the distance plus year effect:

mu.y[i] <- b0[month[i]] + b1[month[i]] * Dist_Berm[i] + b12[month[i]] * Dist_Berm[i] * Dist_Berm[i] + b2 * year[i]

y[i] ~ dnorm(mu.y[i], tau.y)  


```{r}
jags.data <- list(y = inund$log_inund,
                  month = inund$Month2,
                  Dist_Berm = inund$scaled_Dist_Berm,
                  year = inund$Year2,
                  N = nrow(inund),
                  n.months = length(unique(inund$Month2)),
                  n.years = length(unique(inund$Year2)))

MCMC.params <- list(n.samples = 10000,
                    n.burnin = 5000,
                    n.thin = 5,
                    n.chains = 5,
                    model.file = "models/Model_Poly2_month_year.txt")

parameters <- c("b0", "b1", "b2", "b12", "sigma.y",
                 "fit", "fit.new", "deviance")

if (!file.exists("RData/Poly2_month_year.rds")){
  jm.2 <- jags(data = jags.data,
               #inits = inits,
               parameters.to.save= parameters,
               model.file = MCMC.params$model.file,
               n.chains = MCMC.params$n.chains,
               n.burnin = MCMC.params$n.burnin,
               n.thin = MCMC.params$n.thin,
               n.iter = MCMC.params$n.samples,
               DIC = T, 
               parallel=T)
  
  saveRDS(jm.2, file = "RData/Poly2_month_year.rds")  
} else {
  jm.2 <- readRDS("RData/Poly2_month_year.rds")
}

```


Extract the posterior samples and create plots
```{r}
pred.list.jm.2 <- extract.prediction.poly2(zm = jm.2, 
                                           jags.data = jags.data)

pred.list.jm.2$pred.df %>% 
  mutate(Month = ifelse(Month2 < 4, Month2 + 9, Month2 - 3),
         Month_f = factor(Month, 
                          levels = c("10", "11", "12", "1", "2", "3", "4"))) -> pred.df.jm.2

ggplot() + 
  geom_point(data = inund,
             aes(x = scaled_Dist_Berm,
                 y = log(InundHeight_AbvLAT))) +
  geom_path(data = pred.df.jm.2,
            aes(x = Dist_Berm,
                 y = (pred_med))) +
  geom_ribbon(data = pred.df.jm.2,
              aes(x = Dist_Berm,
                  ymin = (pred_low),
                  ymax = (pred_high)),
              alpha = 0.5) +
   geom_point(data = nest.data,
              aes(x = scaled_Dist_Berm,
                  y = log(Nest_Elevation),
                  color = rate_success)) +
  facet_grid(Year ~ Month_f)  

ggsave(filename = "figures/poly2_success.png", 
       dpi = 600, device = "png")

```

Now we add nest locations on top of these plots.

```{r}


```

