---
title: "R Notebook"
output: html_notebook
---

In this Notebook, I use the second-order polynomial function fitted to the inundation data in Inundation_v2.Rmd to evaluate probabilities of inundation for nests. This version (v1.1) computes new measures:

1. Compute proportions of phase-1 deaths (Yes, and to adjust proportion (%) of phase 1 deaths from % of failed eggs to % of total eggs recovered for each nest) for all nests. Then look at how they are affected by the inundation line for the first 30 days of incubation. I'm envisioning this to be plots similar to the last ones but change the hatch success to proportion of phase-1 deaths.

2.   For each nest, compute the height above inundation line (+/- 95% confidence intervals). 

Yep, that’d be great and yes, for max inundation heights for each of the 3 months post laying. These curves look good.


Load essential libraries first.

```{r}
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(readr)
library(lubridate)
library(jagsUI)
library(bayesplot)

source("Dunstan_Inundation_fcns.R")
```

And load the data.

```{r}

inund.cols <- cols(
   Transect = col_double(),
   Post = col_double(),
   InundHeight_AbvLAT = col_double(),
   Dist_Berm = col_double(),
   Berm_elevation = col_double(),
   BermSurvey_Month = col_character(),
   Inund_Month = col_character(),
   Date = col_date(format = "%d/%m/%Y"),
   Time = col_time(format = "%H:%M:%S %p"))

inund <- read_csv("data/inundationRaine.csv", col_types = inund.cols)
min.Dist <- min(inund$Dist_Berm)
sd.Dist <- sqrt(var(inund$Dist_Berm))

inund %>% mutate(Year = ifelse(Date < as.Date("2018-05-01"), 2018, 2019)) %>%
  mutate(Month = month(Date)) %>%
  filter(Transect != 2) %>%
  mutate(Transect_f = as.factor(Transect),
         Year2 = ifelse(Year == 2018, 1, 2),
         Month2 = ifelse(Month > 9, Month - 9, Month + 3),
         Month_f = factor(Month, levels = c("10", "11", "12", "1", "2", "3", "4")),
         Transect2 = Transect - 1,
         log_inund = log(InundHeight_AbvLAT),
         scaled_Dist_Berm = (Dist_Berm - min.Dist)/sd.Dist) -> inund

inund.2018 <- filter(inund, Year == 2018)
inund.2019 <- filter(inund, Year == 2019)

#View(inund)
# Replaced Feb-18 with 15/02/2018 (TE, 2020-03-19)
# Replaced Dec-18 with 15/12/2018 (TE, 2020-03-19)
# Replaced Feb-20 with 15/02/2020 (TE, 2020-03-19)

nest.cols <- cols(fid = col_integer(), 
                  Nest_UID = col_character(), 
                  Northings = col_double(), 
                  Eastings = col_double(), 
                  Nest_Elevation = col_double(),
                  Berm_Dist = col_double(),
                  Date_laid = col_date(format = "%d/%m/%Y"),
                  Date_dug = col_date(format = "%d/%m/%Y"),
                  Sector = col_character(),
                  Habitat = col_character(),
                  Hatched = col_integer(),
                  Live_hatchlings = col_integer(),
                  Dead_hatchlings = col_integer(),
                  Phase_1 = col_integer(),
                  Phase_2 = col_integer(),
                  Phase_3 = col_integer(),
                  Phase_4 = col_integer(),
                  Phase_5 = col_integer(),
                  Phase_6 = col_integer(),
                  Decomposed = col_integer(),
                  Total_unhatched = col_integer(),
                  Total_clutch = col_integer(),
                  rate_success = col_double())

nest.data <- read_csv("data/hatchsuccess_inund_TE.csv", 
                      col_types = nest.cols)

nest.data %>% mutate(Year = ifelse(Date_laid < as.Date("2018-05-01"), 2018, 2019)) %>%
  mutate(Month = month(Date_laid),
         Month2 = ifelse(Month > 9, Month - 9, Month + 3),
         Month_f = factor(Month, levels = c("10", "11", "12", "1", "2", "3", "4")),
         scaled_Dist_Berm = (Berm_Dist - min.Dist)/sd.Dist,
         Phase_1_death = Phase_1/Total_clutch,
         Phase_2_death = Phase_2/Total_clutch) -> nest.data

```


Second order polynomial with month-specific intercept and coefficients for the distance plus year effect:

mu.y[i] <- b0[month[i], year[i]] + b1[month[i]] * Dist_Berm[i] + b12[month[i]] * Dist_Berm[i] * Dist_Berm[i]

y[i] ~ dnorm(mu.y[i], tau.y)  

Results of model fitting is saved in a .rds file (ran in inundation_Nests_v1.Rmd).
```{r}
jags.data <- list(y = inund$log_inund,
                  month = inund$Month2,
                  Dist_Berm = inund$scaled_Dist_Berm,
                  year = inund$Year2,
                  N = nrow(inund),
                  n.months = length(unique(inund$Month2)),
                  n.years = length(unique(inund$Year2)))

MCMC.params <- list(n.samples = 10000,
                    n.burnin = 5000,
                    n.thin = 5,
                    n.chains = 5,
                    model.file = "models/Model_Poly2_1_month_year.txt")

parameters <- c("b0", "b1", "b2", "b12", "sigma.y",
                 "fit", "fit.new", "deviance")

jm.2 <- readRDS("RData/Poly2_1_month_year.rds")

```


Extract the posterior samples and create plots
```{r}
pred.list.jm.2 <- extract.prediction.poly2.1(zm = jm.2, 
                                           jags.data = jags.data)

pred.list.jm.2$pred.df %>% 
  mutate(Month = ifelse(Month2 < 4, Month2 + 9, Month2 - 3),
         Month_f = factor(Month, 
                          levels = c("10", "11", "12", 
                                     "1", "2", "3", "4"))) -> pred.df.jm.2

ggplot() + 
   geom_point(data = nest.data,
              aes(x = scaled_Dist_Berm,
                  y = (Nest_Elevation),
                  color = Phase_1_death),
              alpha = 0.5) +
  geom_point(data = inund,
             aes(x = scaled_Dist_Berm,
                 y = (InundHeight_AbvLAT)),
             color = "red") +
  geom_path(data = pred.df.jm.2,
            aes(x = Dist_Berm,
                 y = exp(pred_med))) +
  geom_ribbon(data = pred.df.jm.2,
              aes(x = Dist_Berm,
                  ymin = exp(pred_low),
                  ymax = exp(pred_high)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Date laid + Phase 1")

# ggsave(filename = "figures/poly2_success.png",
#        dpi = 600, device = "png",
#        height = 3.53, width = 5.73)

```

There may be some patterns of high phase 1 mortality below regression lines? Let's try measuring the distance between each nest and the regression line.

Phase 2?
```{r}
ggplot() + 
   geom_point(data = nest.data,
              aes(x = scaled_Dist_Berm,
                  y = (Nest_Elevation),
                  color = Phase_2_death),
              alpha = 0.5) +
  geom_point(data = inund,
             aes(x = scaled_Dist_Berm,
                 y = (InundHeight_AbvLAT)),
             color = "red") +
  geom_path(data = pred.df.jm.2,
            aes(x = Dist_Berm,
                 y = exp(pred_med))) +
  geom_ribbon(data = pred.df.jm.2,
              aes(x = Dist_Berm,
                  ymin = exp(pred_low),
                  ymax = exp(pred_high)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Date laid + Phase 2")

```

Not sure why a couple of the proportion are >1...  This is from how total clutch size was computed in the data file. It doesn't make sense but asked a question (2020-04-09). 


```{r}
nest.data %>% select(Month2, Year, scaled_Dist_Berm) %>%
  mutate(Year = ifelse(Year == 2018, 1, 2),
         Month = Month2) -> new.data

pred.data <- predict.poly2.1(zm = jm.2, new.data = new.data)

pred.data$qtiles %>% transmute(log.pred.inund.elev.50 = X50.,
                               log.pred.inund.elev.2.5 = X2.5.,
                               log.pred.inund.elev.97.5 = X97.5.) %>%
  cbind(nest.data) %>%
  mutate(dif.nest.pred = Nest_Elevation - exp(log.pred.inund.elev.50),
         dif.nest.pred.2.5 = Nest_Elevation - exp(log.pred.inund.elev.2.5),
         dif.nest.pred.97.5 = Nest_Elevation - exp(log.pred.inund.elev.97.5),
         pred.inund.elev = exp(log.pred.inund.elev.50),
         pred.inund.elev.2.5 = exp(log.pred.inund.elev.2.5),
         pred.inund.elev.97.5 = exp(log.pred.inund.elev.97.5)) -> nest.data.2

#write.csv(nest.data.2, file = "data/nest_inund_prediction.csv")

ggplot(nest.data.2) + 
  geom_errorbar(aes(x = Nest_Elevation,
                    ymin = pred.inund.elev.2.5,
                    ymax = pred.inund.elev.97.5)) +
  geom_point(aes(x = Nest_Elevation,
                 y = pred.inund.elev,
                 color = Month_f)) 

```

Look at time lag:

Shifting time of nests by 15 days
```{r}
nest.data %>% mutate(laid_15d = Date_laid + 15,
                     laid_30d = Date_laid + 30,
                     laid_45d = Date_laid + 45,
                     laid_60d = Date_laid + 60,
                     Month_15d = month(laid_15d),
                     Month_30d = month(laid_30d),
                     Month_45d = month(laid_45d),
                     Month_60d = month(laid_60d),
                     Month_15d_f = factor(Month_15d, 
                                          levels = c("10", "11", "12", 
                                                     "1", "2", "3", "4")),
                     Month_30d_f = factor(Month_30d, 
                                          levels = c("10", "11", "12", 
                                                     "1", "2", "3", "4")),
                     Month_45d_f = factor(Month_45d, 
                                          levels = c("10", "11", "12", 
                                                     "1", "2", "3", "4")),
                     Month_60d_f = factor(Month_60d, 
                                          levels = c("10", "11", "12", 
                                                     "1", "2", "3", "4"))) -> nest.data

nest.data %>% select(scaled_Dist_Berm, 
                     Nest_Elevation, 
                     Phase_1_death, 
                     Month_15d,
                     Month_15d_f, 
                     Year) %>%
  mutate(Month2 = ifelse(Month_15d > 9, 
                         Month_15d - 9, 
                         Month_15d + 3),
         Month_f = Month_15d_f) -> nest.data.15d

ggplot() + 
   geom_point(data = nest.data.15d,
              aes(x = scaled_Dist_Berm,
                  y = log(Nest_Elevation),
                  color = Phase_1_death),
              alpha = 0.5) +
  geom_point(data = inund,
             aes(x = scaled_Dist_Berm,
                 y = log(InundHeight_AbvLAT)),
             color = "red") +
  geom_path(data = pred.df.jm.2,
            aes(x = Dist_Berm,
                 y = (pred_med))) +
  geom_ribbon(data = pred.df.jm.2,
              aes(x = Dist_Berm,
                  ymin = (pred_low),
                  ymax = (pred_high)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Date laid + 15 days")

```


```{r}
nest.data.15d %>% select(Month2, Year, scaled_Dist_Berm) %>%
  mutate(Year = ifelse(Year == 2018, 1, 2),
         Month = Month2) -> new.data.15d

pred.data.15d <- predict.poly2.1(zm = jm.2, new.data = new.data.15d)

pred.data.15d$qtiles %>% transmute(log.pred.nest.elev.50 = X50.,
                                   log.pred.nest.elev.2.5 = X2.5.,
                                   log.pred.nest.elev.97.5 = X97.5.) %>%
  cbind(nest.data.15d) %>%
  mutate(dif.nest.pred = Nest_Elevation - exp(log.pred.nest.elev.50)) -> nest.data.15d

ggplot(nest.data.15d) + 
  geom_point(aes(x = dif.nest.pred,
                 y = Phase_1_death))


```

Shifting time of nests by 30 days

```{r}
nest.data %>% select(scaled_Dist_Berm, 
                     Nest_Elevation, 
                     Phase_1_death, 
                     Month_30d,
                     Month_30d_f, 
                     Year) %>%
  mutate(Month2 = ifelse(Month_30d > 9, 
                         Month_30d - 9, 
                         Month_30d + 3),
         Month_f = Month_30d_f) -> nest.data.30d

ggplot() + 
   geom_point(data = nest.data.30d,
              aes(x = scaled_Dist_Berm,
                  y = log(Nest_Elevation),
                  color = Phase_1_death),
              alpha = 0.5) +
  geom_point(data = inund,
             aes(x = scaled_Dist_Berm,
                 y = log(InundHeight_AbvLAT)),
             color = "red") +
  geom_path(data = pred.df.jm.2,
            aes(x = Dist_Berm,
                 y = (pred_med))) +
  geom_ribbon(data = pred.df.jm.2,
              aes(x = Dist_Berm,
                  ymin = (pred_low),
                  ymax = (pred_high)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Date laid + 30 days")

```



```{r}

nest.data.30d %>% select(Month2, Year, scaled_Dist_Berm) %>%
  mutate(Year = ifelse(Year == 2018, 1, 2),
         Month = Month2) -> new.data.30d

pred.data.30d <- predict.poly2.1(zm = jm.2, new.data = new.data.30d)

pred.data.30d$qtiles %>% transmute(log.pred.nest.elev.50 = X50.,
                                   log.pred.nest.elev.2.5 = X2.5.,
                                   log.pred.nest.elev.97.5 = X97.5.) %>%
  cbind(nest.data.30d) %>%
  mutate(dif.nest.pred = Nest_Elevation - exp(log.pred.nest.elev.50)) -> nest.data.30d

ggplot(nest.data.30d) + 
  geom_point(aes(x = dif.nest.pred,
                 y = Phase_1_death))


```

There is no obvious pattern... 

```{r}

ggplot() + 
   geom_point(data = nest.data.30d,
              aes(x = scaled_Dist_Berm,
                  y = log(Nest_Elevation),
                  color = Phase_1_death),
              alpha = 0.5) +
  geom_point(data = inund,
             aes(x = scaled_Dist_Berm,
                 y = log(InundHeight_AbvLAT)),
             color = "red") +
  geom_path(data = pred.df.jm.2,
            aes(x = Dist_Berm,
                 y = (pred_med))) +
  geom_ribbon(data = pred.df.jm.2,
              aes(x = Dist_Berm,
                  ymin = (pred_low),
                  ymax = (pred_high)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Date laid + 30 days")

# ggsave(filename = "figures/poly2_success_30d.png",
#        dpi = 600, device = "png",
#        height = 3.53, width = 5.73)

```

```{r}
nest.data %>% select(scaled_Dist_Berm, 
                     Nest_Elevation, 
                     rate_success, 
                     Month_45d_f,
                     Year) %>%
  mutate(Month_f = Month_45d_f) -> nest.data.45d

ggplot() + 
   geom_point(data = nest.data.45d,
              aes(x = scaled_Dist_Berm,
                  y = log(Nest_Elevation),
                  color = rate_success),
              alpha = 0.5) +
  geom_point(data = inund,
             aes(x = scaled_Dist_Berm,
                 y = log(InundHeight_AbvLAT)),
             color = "red") +
  geom_path(data = pred.df.jm.2,
            aes(x = Dist_Berm,
                 y = (pred_med))) +
  geom_ribbon(data = pred.df.jm.2,
              aes(x = Dist_Berm,
                  ymin = (pred_low),
                  ymax = (pred_high)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Date laid + 45 days")

# ggsave(filename = "figures/poly2_success_45d.png",
#        dpi = 600, device = "png",
#        height = 3.53, width = 5.73)

```


```{r}
nest.data %>% select(scaled_Dist_Berm, 
                     Nest_Elevation, 
                     rate_success, 
                     Month_60d_f,
                     Year) %>%
  mutate(Month_f = Month_60d_f) -> nest.data.60d

ggplot() + 
   geom_point(data = nest.data.60d,
              aes(x = scaled_Dist_Berm,
                  y = log(Nest_Elevation),
                  color = rate_success),
              alpha = 0.5) +
  geom_point(data = inund,
             aes(x = scaled_Dist_Berm,
                 y = log(InundHeight_AbvLAT)),
             color = "red") +
  geom_path(data = pred.df.jm.2,
            aes(x = Dist_Berm,
                 y = (pred_med))) +
  geom_ribbon(data = pred.df.jm.2,
              aes(x = Dist_Berm,
                  ymin = (pred_low),
                  ymax = (pred_high)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Date laid + 60 days")

# ggsave(filename = "figures/poly2_success_60d.png",
#        dpi = 600, device = "png",
#        height = 3.53, width = 5.73)

```

