---
title: "R Notebook"
output: html_notebook
---

In this Notebook, I use the second-order polynomial function fitted to the inundation data in Inundation_v2.Rmd to evaluate probabilities of inundation for nests. This version (v.2) computes new measures:

1. Compute proportions of phase-1 deaths (Yes, and to adjust proportion (%) of phase 1 deaths from % of failed eggs to % of total eggs recovered for each nest) for all nests. Then look at how they are affected by the inundation line for the first 30 days of incubation. I'm envisioning this to be plots similar to the last ones but change the hatch success to proportion of phase-1 deaths.

2.   For each nest, compute the height above inundation line (+/- 95% confidence intervals). 

Yep, that’d be great and yes, for max inundation heights for each of the 3 months post laying. These curves look good.

For this version (v.3), I try to fulfill the following request from Owen Coffee (2020-08-04):

"The updated inundation logger .csv now contains the inundation heights for all highs in a month above the median (each max in the tidal cycle + ~ 2 days either side) not just the max as was previously used. As you have said, bottom/mid/complete can be calculated from each individual nest depth so really the difference in the analysis is now not just determining inundation from the max monthly high for each incubation month, but how many of the identified highs above median for each month (1st, 2nd and 3rd month of incubation) would correspond with each of bottom/mid/complete inundation for the considered nests. The hope would then be to estimate the total period immersed for each of those inundation events from what Andy is working on, and then whether the timing (early/mid/late development), frequency or period of inundation correlates with clutch mortality."

I'm still unclear on exactly what he's asking... but looking at the data may help. 

Load essential libraries first.

```{r}
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(readr)
library(lubridate)
library(jagsUI)
library(bayesplot)
library(party)
#library(rfPermute)
#library(randomForestExplainer)
source("Dunstan_Inundation_fcns.R")
```

And load the data.

```{r}
#Transect,Post,Date,Time,Aspect,Survey Date,Inundation Month,Dist_from_Berm,Beach_Elevation,Inund_Height
inund.cols <- cols(
   Transect = col_double(),
   Post = col_double(),
   Date = col_date(format = "%d/%m/%Y"),
   Time = col_time(format = "%H:%M:%S %p"),
   Aspect = col_character(),
   Survey_Date = col_character(),
   Inundation_Month = col_character(),
   Dist_from_Berm = col_double(),
   Beach_Elevation = col_double(),
   Inund_Height = col_double())

inund <- read_csv("data/inundationRaine_abovemedian.csv", col_types = inund.cols)
min.Dist <- min(inund$Dist_from_Berm)
sd.Dist <- sqrt(var(inund$Dist_from_Berm))

inund %>% mutate(Year = ifelse(Date < as.Date("2018-05-01"), 2018, 2019)) %>%
  mutate(Month = month(Date)) %>%
  filter(Transect != 2) %>%
  mutate(Transect_f = as.factor(Transect),
         Year2 = ifelse(Year == 2018, 1, 2),
         Month2 = ifelse(Month > 9, Month - 9, Month + 3),
         Month_f = factor(Month, levels = c("10", "11", "12", "1", "2", "3", "4")),
         Transect2 = Transect - 1,
         log_inund = log(Inund_Height),
         scaled_Dist_Berm = (Dist_from_Berm - min.Dist)/sd.Dist) -> inund

inund.2018 <- filter(inund, Year == 2018)
inund.2019 <- filter(inund, Year == 2019)

#View(inund)
# Replaced Feb-18 with 15/02/2018 (TE, 2020-03-19)
# Replaced Dec-18 with 15/12/2018 (TE, 2020-03-19)
# Replaced Feb-20 with 15/02/2020 (TE, 2020-03-19)
#fid,Nest_UID,Northings,Eastings,Aspect,Nest_Elevation,Berm_Dist,Date_laid,Date_dug,Sector,Habitat,Hatched,Live_hatchlings,Dead_hatchlings,Phase_1,Phase_2,Phase_3,Phase_4,Phase_5,Phase_6,Decomposed,Total_unhatched,Total_clutch,rate_success,Season_Peakpop

nest.cols <- cols(fid = col_integer(), 
                  Nest_UID = col_character(), 
                  Northings = col_double(), 
                  Eastings = col_double(), 
                  Aspect = col_character(),
                  Nest_Elevation = col_double(),
                  Berm_Dist = col_double(),
                  Date_laid = col_date(format = "%d/%m/%Y"),
                  Date_dug = col_date(format = "%d/%m/%Y"),
                  Sector = col_character(),
                  Habitat = col_character(),
                  Hatched = col_integer(),
                  Live_hatchlings = col_integer(),
                  Dead_hatchlings = col_integer(),
                  Phase_1 = col_integer(),
                  Phase_2 = col_integer(),
                  Phase_3 = col_integer(),
                  Phase_4 = col_integer(),
                  Phase_5 = col_integer(),
                  Phase_6 = col_integer(),
                  Decomposed = col_integer(),
                  Total_unhatched = col_integer(),
                  Total_clutch = col_integer(),
                  rate_success = col_double(),
                  Season_Peakpop = col_integer())

# the following file was created from revised data from Owen Coffee (nest_inund_prediction_OCedits.csv).
nest.data <- read_csv("data/hatchsuccess_inund.csv", 
                      col_types = nest.cols)

nest.data %>% mutate(Year = ifelse(Date_laid < as.Date("2018-05-01"), 2018, 2019)) %>%
  mutate(Month = month(Date_laid),
         Month2 = ifelse(Month > 9, Month - 9, Month + 3),
         Month_f = factor(Month, levels = c("10", "11", "12", "1", "2", "3", "4")),
         scaled_Dist_Berm = (Berm_Dist - min.Dist)/sd.Dist,
         Phase_1_death = Phase_1/Total_clutch,
         Phase_2_death = Phase_2/Total_clutch) -> nest.data

```


Second order polynomial with month-specific intercept and coefficients for the distance plus year effect:

mu.y[i] <- b0[month[i], year[i]] + b1[month[i]] * Dist_Berm[i] + b12[month[i]] * Dist_Berm[i] * Dist_Berm[i]

y[i] ~ dnorm(mu.y[i], tau.y)  

Results of model fitting is saved in a .rds file (ran in inundation_Nests_v2.Rmd).
```{r}
jags.data <- list(y = inund$log_inund,
                  month = inund$Month2,
                  Dist_Berm = inund$scaled_Dist_Berm,
                  year = inund$Year2,
                  N = nrow(inund),
                  n.months = length(unique(inund$Month2)),
                  n.years = length(unique(inund$Year2)))

MCMC.params <- list(n.samples = 10000,
                    n.burnin = 5000,
                    n.thin = 5,
                    n.chains = 5,
                    model.file = "models/Model_Poly2_1_month_year.txt") 

#model.file = "models/Model_Poly2_month_year.txt")

parameters <- c("b0", "b1", "b2", "b12", "sigma.y",
                 "fit", "fit.new", "deviance")

jm.2_1 <- readRDS("RData/Poly2_1_month_year.rds")

```


Extract the posterior samples and create plots
```{r}
pred.list.jm.2 <- extract.prediction.poly2.1(zm = jm.2_1, 
                                           jags.data = jags.data)

pred.list.jm.2$pred.df %>% 
  mutate(Month = ifelse(Month2 < 4, Month2 + 9, Month2 - 3),
         Month_f = factor(Month, 
                          levels = c("10", "11", "12", 
                                     "1", "2", "3", "4"))) -> pred.df.jm.2

p.1 <- ggplot() + 
   geom_point(data = nest.data,
              aes(x = scaled_Dist_Berm,
                  y = log(Nest_Elevation),
                  color = Phase_1_death),
              alpha = 0.5) +
  geom_point(data = inund,
             aes(x = scaled_Dist_Berm,
                 y = log_inund),
             color = "red") +
  geom_path(data = pred.df.jm.2,
            aes(x = Dist_Berm,
                 y = (pred_med))) +
  geom_ribbon(data = pred.df.jm.2,
              aes(x = Dist_Berm,
                  ymin = (pred_low),
                  ymax = (pred_high)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Predicted inundation height and phase 1 deaths")

# ggsave(plot = p.1, filename = "figures/inundation_phase1_2020-08-05.png",
#        device = "png", dpi = 600)

p.1
```

There may be some patterns of high phase 1 mortality below regression lines? Let's try measuring the distance between each nest and the regression line.

Phase 2?
```{r}
ggplot() + 
   geom_point(data = nest.data,
              aes(x = scaled_Dist_Berm,
                  y = (Nest_Elevation),
                  color = Phase_2_death),
              alpha = 0.5) +
  geom_point(data = inund,
             aes(x = scaled_Dist_Berm,
                 y = (Inund_Height)),
             color = "red") +
  geom_path(data = pred.df.jm.2,
            aes(x = Dist_Berm,
                 y = exp(pred_med))) +
  geom_ribbon(data = pred.df.jm.2,
              aes(x = Dist_Berm,
                  ymin = exp(pred_low),
                  ymax = exp(pred_high)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Date laid + Phase 2")

```

Not sure why a couple of the proportion are >1...  This is from how total clutch size was computed in the data file. It doesn't make sense but asked a question (2020-04-09). This was fixed.


```{r}
nest.data %>% select(Month2, Year, scaled_Dist_Berm) %>%
  mutate(Year = ifelse(Year == 2018, 1, 2),
         Month = Month2) -> new.data

pred.data <- predict.poly2.1(zm = jm.2_1, new.data = new.data)

pred.data$qtiles %>% transmute(log.pred.inund.elev.50 = X50.,
                               log.pred.inund.elev.2.5 = X2.5.,
                               log.pred.inund.elev.97.5 = X97.5.) %>%
  cbind(nest.data) %>%
  mutate(dif.nest.pred = Nest_Elevation - exp(log.pred.inund.elev.50),
         dif.nest.pred.2.5 = Nest_Elevation - exp(log.pred.inund.elev.2.5),
         dif.nest.pred.97.5 = Nest_Elevation - exp(log.pred.inund.elev.97.5),
         pred.inund.elev = exp(log.pred.inund.elev.50),
         pred.inund.elev.2.5 = exp(log.pred.inund.elev.2.5),
         pred.inund.elev.97.5 = exp(log.pred.inund.elev.97.5)) -> nest.data.2

#write.csv(nest.data.2, file = "data/nest_inund_prediction.csv")

ggplot(nest.data.2) + 
  geom_errorbar(aes(x = Berm_Dist,
                    ymin = pred.inund.elev.2.5,
                    ymax = pred.inund.elev.97.5)) +
  geom_point(aes(x = Berm_Dist,
                 y = pred.inund.elev,
                 color = rate_success,
                 shape = as.factor(Year))) 

```

```{r}
ggplot(nest.data.2) + 
  geom_errorbar(aes(x = scaled_Dist_Berm,
                    ymin = dif.nest.pred.2.5,
                    ymax = dif.nest.pred.97.5)) +
  geom_point(aes(x = scaled_Dist_Berm,
                 y = dif.nest.pred,
                 color = rate_success)) 

```



Look at time lag:

Shifting time of nests by 15 days
```{r}
nest.data %>% mutate(laid_15d = Date_laid + 15,
                     laid_30d = Date_laid + 30,
                     laid_45d = Date_laid + 45,
                     laid_60d = Date_laid + 60,
                     Month_15d = month(laid_15d),
                     Month_30d = month(laid_30d),
                     Month_45d = month(laid_45d),
                     Month_60d = month(laid_60d),
                     Month_15d_f = factor(Month_15d, 
                                          levels = c("10", "11", "12", 
                                                     "1", "2", "3", "4")),
                     Month_30d_f = factor(Month_30d, 
                                          levels = c("10", "11", "12", 
                                                     "1", "2", "3", "4")),
                     Month_45d_f = factor(Month_45d, 
                                          levels = c("10", "11", "12", 
                                                     "1", "2", "3", "4")),
                     Month_60d_f = factor(Month_60d, 
                                          levels = c("10", "11", "12", 
                                                     "1", "2", "3", "4"))) -> nest.data

```

Try 30 and 45 days offset. Offset of 15 days is the same as 30 days.

```{r}

nest.data %>% select(fid,
                     Habitat,
                     Berm_Dist,
                     scaled_Dist_Berm, 
                     Nest_Elevation, 
                     Phase_1_death, 
                     rate_success,
                     Total_clutch,
                     Month_30d,
                     Month_30d_f, 
                     Year,
                     Northings,
                     Eastings) %>%
  mutate(Month2 = ifelse(Month_30d > 9, 
                         Month_30d - 9, 
                         Month_30d + 3),
         Month_f = Month_30d_f,
         Northings2 = (Northings - min(Northings))/1000,
         Eastings2 = (Eastings - min(Eastings))/1000) -> nest.data.30d

nest.data.30d %>% 
  select(Month2, Year, scaled_Dist_Berm) %>%
  mutate(Year = ifelse(Year == 2018, 1, 2),
         Month = Month2) -> new.data.30d

pred.data.30d <- predict.poly2.1(zm = jm.2_1, new.data = new.data.30d)

pred.data.30d$qtiles %>% transmute(log.pred.nest.elev.50 = X50.,
                                   log.pred.nest.elev.2.5 = X2.5.,
                                   log.pred.nest.elev.97.5 = X97.5.) %>%
  cbind(nest.data.30d) %>%
  mutate(dif.nest.pred = Nest_Elevation - exp(log.pred.nest.elev.50)) -> nest.data.30d

nest.data %>% select(fid,
                     Habitat,
                     scaled_Dist_Berm, 
                     Nest_Elevation, 
                     rate_success, 
                     Phase_1_death,
                     Month_45d,
                     Month_45d_f,
                     Year) %>%
  mutate(Month2 = ifelse(Month_45d > 9, 
                         Month_45d - 9, 
                         Month_45d + 3),
         Month_f = Month_45d_f) -> nest.data.45d

nest.data.45d %>% select(Month2, Year, scaled_Dist_Berm) %>%
  mutate(Year = ifelse(Year == 2018, 1, 2),
         Month = Month2) -> new.data.45d

pred.data.45d <- predict.poly2.1(zm = jm.2_1, new.data = new.data.45d)

pred.data.45d$qtiles %>% transmute(log.pred.nest.elev.50 = X50.,
                                   log.pred.nest.elev.2.5 = X2.5.,
                                   log.pred.nest.elev.97.5 = X97.5.) %>%
  cbind(nest.data.45d) %>%
  mutate(dif.nest.pred = Nest_Elevation - exp(log.pred.nest.elev.50)) -> nest.data.45d

nest.data.45d %>% select(fid,
                         log.pred.nest.elev.2.5,
                         log.pred.nest.elev.50,
                         log.pred.nest.elev.97.5) %>%
  transmute(fid = fid,
            log.pred.nest.elev.2.5.45d = log.pred.nest.elev.2.5,
            log.pred.nest.elev.50.45d = log.pred.nest.elev.50,
            log.pred.nest.elev.97.5.45d = log.pred.nest.elev.97.5) %>%
  left_join(nest.data.30d, by = "fid") %>%
    transmute(fid = fid,
              log.pred.nest.elev.2.5.30d = log.pred.nest.elev.2.5,
              log.pred.nest.elev.50.30d = log.pred.nest.elev.50,
              log.pred.nest.elev.97.5.30d = log.pred.nest.elev.97.5,              
              log.pred.nest.elev.2.5.45d = log.pred.nest.elev.2.5.45d,
              log.pred.nest.elev.50.45d = log.pred.nest.elev.50.45d,
              log.pred.nest.elev.97.5.45d = log.pred.nest.elev.97.5.45d,
              Habitat = as.factor(Habitat),
              scaled_Dist_Berm = scaled_Dist_Berm, 
              Nest_Elevation = Nest_Elevation, 
              rate_success = rate_success/100, 
              Phase_1_death = Phase_1_death,
              dif_nest_pred = dif.nest.pred,
              Berm_Dist = Berm_Dist,
              Total_Clutch = Total_clutch,
              Year = Year,
              Northings2 = Northings2,
              Eastings2 = Eastings2,
              RV = runif(nrow(nest.data.30d), 0, 1)) -> nest.data.RF


```

Shifting time of nests by 30 days

```{r}

ggplot() + 
   geom_point(data = nest.data.30d,
              aes(x = scaled_Dist_Berm,
                  y = log(Nest_Elevation),
                  color = Phase_1_death),
              alpha = 0.5) +
  geom_point(data = inund,
             aes(x = scaled_Dist_Berm,
                 y = log(Inund_Height)),
             color = "red") +
  geom_path(data = pred.df.jm.2,
            aes(x = Dist_Berm,
                 y = (pred_med))) +
  geom_ribbon(data = pred.df.jm.2,
              aes(x = Dist_Berm,
                  ymin = (pred_low),
                  ymax = (pred_high)),
              alpha = 0.5) +
  facet_grid(Year ~ Month_f) + 
  labs(title = "Date laid + 30 days")

# ggsave(filename = "figures/poly2_success_30d.png",
#        dpi = 600, device = "png",
#        height = 3.53, width = 5.73)


```


```{r}

ggplot(nest.data.30d) + 
  geom_point(aes(x = dif.nest.pred,
                 y = Phase_1_death))

```

There is no obvious pattern... 

Can we predict Phase_1_death with all possible variables using random forest?

```{r}
ntree <- 500

M.1 <- as.formula("Phase_1_death ~ scaled_Dist_Berm + 
                    Berm_Dist + 
                    Total_Clutch +
                  Habitat +
                  Year +
                  Nest_Elevation + 
                  log.pred.nest.elev.50.30d + 
                  log.pred.nest.elev.2.5.30d + 
                  log.pred.nest.elev.97.5.30d +
                  log.pred.nest.elev.50.45d + 
                  log.pred.nest.elev.2.5.45d + 
                  log.pred.nest.elev.97.5.45d +
                  dif_nest_pred +
                  Northings2 +
                  Eastings2 +
                  RV")

if (!file.exists("RData/RF_M_1_out.rds")){
  RF.M.1 <- cforest(formula = M.1,
                    data = nest.data.RF,
                    control = cforest_unbiased(ntree = ntree,
                                               trace = 500))
  saveRDS(RF.M.1, file = "RData/RF_M_1_out.rds")
} else {
  RF.M.1 <- readRDS("RData/RF_M_1_out.rds")
}

if (!file.exists("RData/RF_M_1_varImp.rds")){
  var.imp <- sort(varimp(RF.M.1), decreasing = FALSE)
  saveRDS(var.imp, file = "RData/RF_M_1_varImp.rds")
} else {
  var.imp <- readRDS("RData/RF_M_1_varImp.rds")
}

if (!file.exists("RData/RF_M_1_predict.rds")){
  pred.RF.M.1 <- predict(RF.M.1, newdata = NULL)
  saveRDS(pred.RF.M.1, file = "RData/RF_M_1_predict.rds")
} else {
  pred.RF.M.1 <- readRDS("RData/RF_M_1_predict.rds")
}

```


Look at the variable importance:
```{r}
var.imp.df <- data.frame(var.imp)
var.imp.df$Variable <- rownames(var.imp.df)

ggplot(data = var.imp.df) + 
  geom_point(aes(x = var.imp, y = reorder(Variable, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))
```

Difference in nest height and nest elevations are important. 

```{r}
M.1.1 <- as.formula("Phase_1_death ~ scaled_Dist_Berm + 
                    Berm_Dist + 
                    Habitat +
                    Nest_Elevation + 
                    log.pred.nest.elev.2.5.30d + 
                    dif_nest_pred +
                    Eastings2 +
                    RV")

if (!file.exists("RData/RF_M_1_1_out.rds")){
  RF.M.1.1 <- cforest(formula = M.1.1,
                      data = nest.data.RF,
                      control = cforest_unbiased(ntree = ntree,
                                                 trace = 500))
  saveRDS(RF.M.1.1, file = "RData/RF_M_1_1_out.rds")
} else {
  RF.M.1.1 <- readRDS("RData/RF_M_1_1_out.rds")
}

if (!file.exists("RData/RF_M_1_1_varImp.rds")){
  var.imp.1.1 <- sort(varimp(RF.M.1.1), decreasing = FALSE)
  saveRDS(var.imp.1.1, file = "RData/RF_M_1_1_varImp.rds")
} else {
  var.imp.1.1 <- readRDS("RData/RF_M_1_1_varImp.rds")
}

if (!file.exists("RData/RF_M_1_1_predict.rds")){
  pred.RF.M.1.1 <- predict(RF.M.1.1, newdata = NULL)
  saveRDS(pred.RF.M.1.1, file = "RData/RF_M_1_1_predict.rds")
} else {
  pred.RF.M.1.1 <- readRDS("RData/RF_M_1_1_predict.rds")
}
```


Look at the variable importance:
```{r}
var.imp.df <- data.frame(var.imp.1.1)
var.imp.df$Variable <- rownames(var.imp.df)

ggplot(data = var.imp.df) + 
  geom_point(aes(x = var.imp.1.1, 
                 y = reorder(Variable, var.imp.1.1)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))

#ggsave(filename = "figures/varImp_RF_M1.png", device = "png", dpi = 600)
```

Compare the data and predictions:

```{r}
nest.data.RF$Phase_1_death_prediction <- pred.RF.M.1.1[,1]
ggplot(data = nest.data.RF) +
  geom_point(aes(x = Phase_1_death, 
                 y = Phase_1_death_prediction)) + 
  geom_abline(slope = 1.0, intercept = 0.0) + 
  ylim(c(0, 1)) + 
  labs(x = "Observed phase 1 death", 
       y = "Predicted phase 1 death")

#ggsave(filename = "figures/RF_M1_prediction.png", device = "png", dpi = 600)
```


This doesn't look so good... There is a positive relationship but not very strong... 

What about overall hatching success?

```{r}
M.2 <- as.formula("rate_success ~ scaled_Dist_Berm + 
                  Berm_Dist + 
                  Total_Clutch +
                  Habitat +
                  Nest_Elevation + 
                  log.pred.nest.elev.50.30d + 
                  log.pred.nest.elev.2.5.30d + 
                  log.pred.nest.elev.97.5.30d +
                  log.pred.nest.elev.50.45d + 
                  log.pred.nest.elev.2.5.45d + 
                  log.pred.nest.elev.97.5.45d +
                  dif_nest_pred +
                  Year +
                  Northings2 +
                  Eastings2 +
                  RV")

if (!file.exists("RData/RF_M_2_out.rds")){
  RF.M.2 <- cforest(formula = M.2,
                    data = nest.data.RF,
                    control = cforest_unbiased(ntree = ntree,
                                               trace = 500))
  saveRDS(RF.M.2, file = "RData/RF_M_2_out.rds")
} else {
  RF.M.2 <- readRDS("RData/RF_M_2_out.rds")
}

if (!file.exists("RData/RF_M_2_varImp.rds")){
  var.imp.M.2 <- sort(varimp(RF.M.2), decreasing = FALSE)
  saveRDS(var.imp.M.2, file = "RData/RF_M_2_varImp.rds")
} else {
  var.imp.M.2 <- readRDS("RData/RF_M_2_varImp.rds")
}

if (!file.exists("RData/RF_M_2_predict.rds")){
  pred.RF.M.2 <- predict(RF.M.2, newdata = NULL)
  saveRDS(pred.RF.M.2, file = "RData/RF_M_2_predict.rds")
} else {
  pred.RF.M.2 <- readRDS("RData/RF_M_2_predict.rds")
}

```



Look at the variable importance:
```{r}
var.imp.M.2.df <- data.frame(var.imp.M.2)
var.imp.M.2.df$Variable <- rownames(var.imp.M.2.df)

ggplot(data = var.imp.M.2.df) + 
  geom_point(aes(x = var.imp, y = reorder(Variable, var.imp)),
             size = 3) + 
  theme_bw() + 
  labs(x = "Variable importance") + 
  theme(axis.title.y = element_blank(),
        axis.title.x = element_text(size =12))
```

Difference in nest height and predicted inundation level and nest elevation are important. Again, a lot of useless variables. So, remove...


```{r}
M.2.2 <- as.formula("rate_success ~ scaled_Dist_Berm + 
                  Berm_Dist + 
                  Total_Clutch +
                  Habitat +
                  Nest_Elevation + 
                  log.pred.nest.elev.2.5.45d + 
                  dif_nest_pred +
                  Year +
                  Eastings2 +
                  RV")

if (!file.exists("RData/RF_M_2_2_out.rds")){
  RF.M.2.2 <- cforest(formula = M.2.2,
                    data = nest.data.RF,
                    control = cforest_unbiased(ntree = ntree,
                                               trace = 500))
  saveRDS(RF.M.2.2, file = "RData/RF_M_2_2_out.rds")
} else {
  RF.M.2.2 <- readRDS("RData/RF_M_2_2_out.rds")
}

if (!file.exists("RData/RF_M_2_2_varImp.rds")){
  var.imp.M.2.2 <- sort(varimp(RF.M.2.2), decreasing = FALSE)
  saveRDS(var.imp.M.2.2, file = "RData/RF_M_2_2_varImp.rds")
} else {
  var.imp.M.2.2 <- readRDS("RData/RF_M_2_2_varImp.rds")
}

if (!file.exists("RData/RF_M_2_2_predict.rds")){
  pred.RF.M.2.2 <- predict(RF.M.2.2, newdata = NULL)
  saveRDS(pred.RF.M.2.2, file = "RData/RF_M_2_2_predict.rds")
} else {
  pred.RF.M.2.2 <- readRDS("RData/RF_M_2_2_predict.rds")
}

```


Compare the data and predictions:

```{r}
nest.data.RF$rate_success_prediction <- pred.RF.M.2.2[,1]
ggplot(data = nest.data.RF) +
  geom_point(aes(x = rate_success, y = rate_success_prediction)) + 
  geom_abline(slope = 1.0, intercept = 0.0) + 
  ylim(c(0, 1)) + 
  labs(x = "Observed success rate", 
       y = "Predicted success rate")

```

About the same as the Phase 1 deaths... 

